---
title: "Chile"
author: "Luisa Olaya"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


knitr::opts_chunk$set(echo = TRUE)
set.seed(42) #for consistent results
library(haven)
library(foreign)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stargazer)
library(naniar)
library(car)
library(carData)
library(FactoMineR)
library(factoextra)

Chile <-read.csv("/Users/mac/Desktop/wORKING dIRECTORY/prgchlp1.csv", header=T, na.strings=c(""))

```

## R Markdown

<br>

**First steps: preparing the data **

1. Selection of variables per group of skills ICT, Numeracy and Literacy

2. Identification of NAs in the possible independent variables (all those that signal income) for this the explored variables were YEARLYINCPR, EARNMTHPPP, EARNHR, EARNHRBONUS, EARNHRBONUSPPP. What we found was that almost all of them have at least 2847 NAs or V that stands in the data ser for valid skip. Thus, taking into account that this is the most important variable of our study we reduced the data set to the number of observations that reported something in the variable YEARLYINCPR, which reduces our data set from 6306 observations to 3459. 

3. More over we analyed the number of NAs or V in the other variables selected. The main findings were that ICT skills are the ones with more missings. 
--> For ICT skills in work they have 1176 Vs out of 2382 observations. 
--> For ICT skills in daily life 859 Vs  and one N out of 2382 observations. 

--> However more general questions about the use of computer and whose answers were limited to (yes/no) such as computer COMPUTEREXPERIENCE had only 2 NAs and no Vs

--> Computer experience in job G_Q04 and G_Q04_T were complete

--> Computer experience in daily life H_Q04a registered 1206 V and H_Q04b 364 V


<br>

```{r cars}


newChile <- Chile %>% 
  select("AGE_R", "GENDER_R","B_Q01a", "B_Q01a_T", "B_Q02a", "B_Q02c", "B_Q10c", "B_Q01b", "C_Q01a", "C_Q01c", "C_Q02a", "D_Q03", "D_Q14", "D_Q16a", "D_Q18a_T", "F_Q01b","F_Q02b","F_Q02c","F_Q02d","F_Q02e","F_Q03b","F_Q04a","F_Q04b","F_Q05a","F_Q05b","F_Q07b","G_Q01a","G_Q02a","G_Q02b","G_Q02c","G_Q02d","G_Q03b","G_Q03c","G_Q03d","G_Q03f","G_Q03g","G_Q03h", "G_Q04", "G_Q04_T" , "G_Q05a", "G_Q05c", "G_Q05d", "G_Q05e", "G_Q05g", "G_Q05h", "G_Q06", "G_Q07", "G_Q08", "H_Q01a", "H_Q01b", "H_Q01b_T", "H_Q01c", "H_Q01c_T", "H_Q01d", "H_Q01e", "H_Q01e_T", "H_Q01f", "H_Q01g", "H_Q01h", "H_Q02a", "H_Q02b","H_Q02c", "H_Q02d", "H_Q03b", "H_Q03c", "H_Q03d", "H_Q03f", "H_Q03g", "H_Q03h","H_Q04a", "H_Q04b", "H_Q05a", "H_Q05c", "H_Q05d", "H_Q05e", "H_Q05f", "H_Q05g", "H_Q05h", "J_Q03a", "J_Q03b", "J_Q06b", "J_Q07b","COMPUTEREXPERIENCE", "MONTHLYINCPR","YEARLYINCPR", "REG_TL2")

## Missing variables
##Vsualizarion of missing variables

gg_miss_var(newChile)


table(is.na(newChile$YEARLYINCPR))

table(is.na(newChile$MONTHLYINCPR))

#droping NAs from the independent variable 


newChile1 <- drop_na(newChile, MONTHLYINCPR)

# Number of women and men 


barplot(table(newChile1$GENDER_R))
newChile1 %>% count(GENDER_R)

# Education status
newChile1 %>% count(B_Q01a)
newChile1 %>% count(B_Q01a_T)
newChile1 %>% count(B_Q02a)
newChile1 %>% count(B_Q02c) #x - 3224 V ESTA 1
newChile1 %>% count(B_Q10c) #x- 3176 V ESTA 2
newChile1 %>% count(B_Q01b) # 2134 v ESTA 3

# Work status 
newChile1 %>% count(C_Q01a)
newChile1 %>% count(C_Q01c) # 3459 v ESTA 4
newChile1 %>% count(C_Q02a) # 3459 v ESTA 5 
newChile1 %>% count(D_Q03) # D 42 - r21 
newChile1 %>% count(D_Q14) #
newChile1 %>% count(D_Q16a) # V 1008
newChile1 %>% count(D_Q18a_T) # 13 NA 


# ICT skills in Job
newChile1 %>% count(G_Q04) # experience with computer in job yes no Complete
newChile1%>% count(G_Q04_T) # Complete
newChile1 %>% count(COMPUTEREXPERIENCE) #******
newChile1 %>% count(G_Q05a) # 1176 
newChile1 %>% count(G_Q05c) # 1176 + r 1
newChile1%>% count(G_Q05d) # # 1176 
newChile1 %>% count(G_Q05e) # # 1176
newChile1 %>% count(G_Q05g) # # 1176
newChile1%>% count(G_Q05h) # 1176
newChile1%>% count(G_Q06) # 1176
newChile1 %>% count(G_Q07) # 1176 
newChile1 %>% count(G_Q08) # 1176

#ICT skills in daily life
newChile1 %>% count(H_Q04a) # 1206 V + 1 N experience with compiuter every life
newChile1 %>% count(H_Q04b) # 364 + 1 n
newChile1 %>% count(H_Q05a) # 859 V + 1 N   
newChile1 %>% count(H_Q05c) # 859 V + 1 N 
newChile1 %>% count(H_Q05d) # 859 V + 1 N  
newChile1 %>% count(H_Q05e) # 859 V + 1 N 
newChile1 %>% count(H_Q05f) # 859 V + 1 N 
newChile1 %>% count(H_Q05g) # 859 V + 1 N  
newChile1 %>% count(H_Q05h) # 859 V + 1 N  

# Children and parents level of education
newChile1 %>% count(J_Q03a)
newChile1 %>% count(J_Q03b) #943
newChile1 %>% count(J_Q06b) 

# Soft skills 
newChile1 %>% count(F_Q01b) #748
newChile1%>% count(F_Q02b) 
newChile1%>% count(F_Q02c)
newChile1 %>% count(F_Q02d)
newChile1 %>% count(F_Q02e)
newChile1 %>% count(F_Q03b)
newChile1 %>% count(F_Q04a)
newChile1%>% count(F_Q04b)
newChile1 %>% count(F_Q05a)
newChile1 %>% count(F_Q05b)

# Literacy work 
newChile1 %>% count(G_Q01a)
newChile1 %>% count(G_Q02a)
newChile1 %>% count(G_Q02b)
newChile1 %>% count(G_Q02c)
newChile1 %>% count(G_Q02d)

# Numeracy work 
newChile1 %>% count(G_Q03b)
newChile1 %>% count(G_Q03c)
newChile1 %>% count(G_Q03d)
newChile1 %>% count(G_Q03f)
newChile1 %>% count(G_Q03g)
newChile1 %>% count(G_Q03h)

# Literacy life
newChile1 %>% count(H_Q01a)
newChile1 %>% count(H_Q01b)
newChile1 %>% count(H_Q01b_T)
newChile1 %>% count(H_Q01d)
newChile1 %>% count(H_Q01c)
newChile1 %>% count(H_Q01e)
newChile1 %>% count(H_Q01e_T)
newChile1 %>% count(H_Q01f)
newChile1 %>% count(H_Q01g)
newChile1 %>% count(H_Q01h)
newChile1 %>% count(H_Q02a)
newChile1 %>% count(H_Q02b)
newChile1 %>% count(H_Q02c)
newChile1 %>% count(H_Q02d)

# Numeracy life
newChile1 %>% count(H_Q03b)
newChile1 %>% count(H_Q03c)
newChile1 %>% count(H_Q03d)
newChile1 %>% count(H_Q03f)
newChile1 %>% count(H_Q03g)
newChile1 %>% count(H_Q03h)

# Region
newChile1 %>% count(REG_TL2)

## Income variables
Chile %>% count(YEARLYINCPR) #2830
Chile %>% count(EARNMTH) 
Chile %>% count(EARNHR) #2732
Chile %>% count(EARNHRDCL) #2732
Chile %>% count(EARNHRPPP)
Chile %>% count(EARNHRBONUS)#103 ESPACIOS EN BLANCO
Chile %>% count(EARNHRBONUSDCL)
Chile %>% count(EARNHRBONUSPPP) #1033
Chile %>% count(EARNFLAG)


```

<br>

**Adaptation of the dataset **

Since there are non numeric factor in our dataset such as V, N and R we had to convert them in NAs in order to work with thw variables afterwards. 

<br>
```{r pressure, echo=FALSE}

#Gender

newChile1$GENDER_Rn[newChile1$GENDER_R == "1"] = 0
newChile1$GENDER_Rn[newChile1$GENDER_R == "2"] = 1


#B_Q01a
newChile1$B_Q01an[newChile1$B_Q01a == "D"] = NA
newChile1$B_Q01an[newChile1$B_Q01a == "1"] = 1
newChile1$B_Q01an[newChile1$B_Q01a == "2"] = 2
newChile1$B_Q01an[newChile1$B_Q01a == "5"] = 5 
newChile1$B_Q01an[newChile1$B_Q01a == "6"] = 6
newChile1$B_Q01an[newChile1$B_Q01a == "7"] = 7
newChile1$B_Q01an[newChile1$B_Q01a == "11"] = 11
newChile1$B_Q01an[newChile1$B_Q01a == "12"] = 12
newChile1$B_Q01an[newChile1$B_Q01a == "13"] = 13
newChile1$B_Q01an[newChile1$B_Q01a == "14"] = 14
newChile1$B_Q01an[newChile1$B_Q01a == "15"] = 15

#B_Q01a_T

newChile1$B_Q01a_Tn[newChile1$B_Q01a_T == "M"] = NA
newChile1$B_Q01a_Tn[newChile1$B_Q01a_T == "1"] = 1
newChile1$B_Q01a_Tn[newChile1$B_Q01a_T == "2"] = 2
newChile1$B_Q01a_Tn[newChile1$B_Q01a_T == "3"] = 3 
newChile1$B_Q01a_Tn[newChile1$B_Q01a_T == "4"] = 4

#B_Q02a

newChile1$B_Q02an[newChile1$B_Q02a == "R"] = NA
newChile1$B_Q02an[newChile1$B_Q02a == "1"] = 0
newChile1$B_Q02an[newChile1$B_Q02a== "2"] = 1

#B_Q02c
newChile1$B_Q02cn[newChile1$B_Q02c == "V"] = NA
newChile1$B_Q02cn[newChile1$B_Q02c == "1"] = 1
newChile1$B_Q02cn[newChile1$B_Q02c == "2"] = 2
newChile1$B_Q02cn[newChile1$B_Q02c == "3"] = 3
newChile1$B_Q02cn[newChile1$B_Q02c == "4"] = 4
newChile1$B_Q02cn[newChile1$B_Q02c == "5"] = 5
newChile1$B_Q02cn[newChile1$B_Q02c == "6"] = 6
newChile1$B_Q02cn[newChile1$B_Q02c == "7"] = 7
newChile1$B_Q02cn[newChile1$B_Q02c == "8"] = 8
newChile1$B_Q02cn[newChile1$B_Q02c == "9"] = 9 
newChile1$B_Q02cn[newChile1$B_Q02c == "R"] = NA

#B_Q10c

newChile1$B_Q10cn[newChile1$B_Q10c == "V"] = NA
newChile1$B_Q10cn[newChile1$B_Q10c == "1"] = 1
newChile1$B_Q10cn[newChile1$B_Q10c == "2"] = 2
newChile1$B_Q10cn[newChile1$B_Q10c == "3"] = 3
newChile1$B_Q10cn[newChile1$B_Q10c == "4"] = 4

#B_Q01b

newChile1$B_Q01bn[newChile1$B_Q01b == "V"] = NA
newChile1$B_Q01bn[newChile1$B_Q01b == "D"] = NA
newChile1$B_Q01bn[newChile1$B_Q01b == "R"] = NA
newChile1$B_Q01bn[newChile1$B_Q01b == "1"] = 1
newChile1$B_Q01bn[newChile1$B_Q01b == "2"] = 2
newChile1$B_Q01bn[newChile1$B_Q01b == "3"] = 3
newChile1$B_Q01bn[newChile1$B_Q01b == "4"] = 4
newChile1$B_Q01bn[newChile1$B_Q01b == "5"] = 5
newChile1$B_Q01bn[newChile1$B_Q01b == "6"] = 6
newChile1$B_Q01bn[newChile1$B_Q01b == "7"] = 7
newChile1$B_Q01bn[newChile1$B_Q01b == "8"] = 8
newChile1$B_Q01bn[newChile1$B_Q01b == "9"] = 9

# C_Q01c
newChile1$C_Q01cn[newChile1$C_Q01c == "V"] = NA

#C_Q02a

newChile1$C_Q02an[newChile1$C_Q02a == "V"] = NA

#D_Q03

newChile1$D_Q03n[newChile1$D_Q03 == "R"] = NA
newChile1$D_Q03n[newChile1$D_Q03 == "D"] = NA
newChile1$D_Q03n[newChile1$D_Q03 == "1"] = 1
newChile1$D_Q03n[newChile1$D_Q03 == "2"] = 2
newChile1$D_Q03n[newChile1$D_Q03 == "3"] = 3

#D_Q14

newChile1$D_Q14n[newChile1$D_Q14 == "D"] = NA
newChile1$D_Q14n[newChile1$D_Q14 == "1"] = 1
newChile1$D_Q14n[newChile1$D_Q14 == "2"] = 2
newChile1$D_Q14n[newChile1$D_Q14 == "3"] = 3
newChile1$D_Q14n[newChile1$D_Q14 == "4"] = 4
newChile1$D_Q14n[newChile1$D_Q14 == "5"] = 5

#D_Q16a

newChile1$D_Q16an[newChile1$D_Q16a == "V"] = NA
newChile1$D_Q16an[newChile1$D_Q16a == "1"] = 1
newChile1$D_Q16an[newChile1$D_Q16a == "2"] = 2
newChile1$D_Q16an[newChile1$D_Q16a == "3"] = 3
newChile1$D_Q16an[newChile1$D_Q16a == "4"] = 4
newChile1$D_Q16an[newChile1$D_Q16a == "5"] = 5
newChile1$D_Q16an[newChile1$D_Q16a == "6"] = 6
newChile1$D_Q16an[newChile1$D_Q16a == "7"] = 7

#F_Q01b

newChile1$F_Q01bn[newChile1$F_Q01b== "1"] = 1
newChile1$F_Q01bn[newChile1$F_Q01b== "2"] = 2
newChile1$F_Q01bn[newChile1$F_Q01b== "3"] = 3
newChile1$F_Q01bn[newChile1$F_Q01b== "4"] = 4
newChile1$F_Q01bn[newChile1$F_Q01b== "5"] = 5
newChile1$F_Q01bn[newChile1$F_Q01b== "N"] = NA
newChile1$F_Q01bn[newChile1$F_Q01b== "R"] = NA
newChile1$F_Q01bn[newChile1$F_Q01b== "V"] = NA

#F_Q02b

newChile1$F_Q02bn[newChile1$F_Q02b== "1"] = 1
newChile1$F_Q02bn[newChile1$F_Q02b== "2"] = 2
newChile1$F_Q02bn[newChile1$F_Q02b== "3"] = 3
newChile1$F_Q02bn[newChile1$F_Q02b== "4"] = 4
newChile1$F_Q02bn[newChile1$F_Q02b== "5"] = 5
newChile1$F_Q02bn[newChile1$F_Q02b== "N"] = NA
newChile1$F_Q02bn[newChile1$F_Q02b== "R"] = NA

#F_Q02c

newChile1$F_Q02cn[newChile1$F_Q02c== "1"] = 1
newChile1$F_Q02cn[newChile1$F_Q02c== "2"] = 2
newChile1$F_Q02cn[newChile1$F_Q02c== "3"] = 3
newChile1$F_Q02cn[newChile1$F_Q02c== "4"] = 4
newChile1$F_Q02cn[newChile1$F_Q02c== "5"] = 5
newChile1$F_Q02cn[newChile1$F_Q02c== "N"] = NA
newChile1$F_Q02cn[newChile1$F_Q02c== "R"] = NA

#F_Q02d

newChile1$F_Q02dn[newChile1$F_Q02d== "1"] = 1
newChile1$F_Q02dn[newChile1$F_Q02d== "2"] = 2
newChile1$F_Q02dn[newChile1$F_Q02d== "3"] = 3
newChile1$F_Q02dn[newChile1$F_Q02d== "4"] = 4
newChile1$F_Q02dn[newChile1$F_Q02d== "5"] = 5
newChile1$F_Q02dn[newChile1$F_Q02d== "D"] = NA
newChile1$F_Q02dn[newChile1$F_Q02d== "N"] = NA 
newChile1$F_Q02dn[newChile1$F_Q02d== "R"] = NA

#F_Q02e

newChile1$F_Q02en[newChile1$F_Q02e== "1"] = 1
newChile1$F_Q02en[newChile1$F_Q02e== "2"] = 2
newChile1$F_Q02en[newChile1$F_Q02e== "3"] = 3
newChile1$F_Q02en[newChile1$F_Q02e== "4"] = 4
newChile1$F_Q02en[newChile1$F_Q02e== "5"] = 5
newChile1$F_Q02en[newChile1$F_Q02e== "N"] = NA 
newChile1$F_Q02en[newChile1$F_Q02e== "R"] = NA

#F_Q03b

newChile1$F_Q03bn[newChile1$F_Q03b== "1"] = 1
newChile1$F_Q03bn[newChile1$F_Q03b== "2"] = 2
newChile1$F_Q03bn[newChile1$F_Q03b== "3"] = 3
newChile1$F_Q03bn[newChile1$F_Q03b== "4"] = 4
newChile1$F_Q03bn[newChile1$F_Q03b== "5"] = 5
newChile1$F_Q03bn[newChile1$F_Q03b== "D"] = NA
newChile1$F_Q03bn[newChile1$F_Q03b== "N"] = NA

#F_Q04a

newChile1$F_Q04an[newChile1$F_Q04a== "1"] = 1
newChile1$F_Q04an[newChile1$F_Q04a== "2"] = 2
newChile1$F_Q04an[newChile1$F_Q04a== "3"] = 3
newChile1$F_Q04an[newChile1$F_Q04a== "4"] = 4
newChile1$F_Q04an[newChile1$F_Q04a== "5"] = 5
newChile1$F_Q04an[newChile1$F_Q04a== "D"] = NA
newChile1$F_Q04an[newChile1$F_Q04a== "N"] = NA

#F_Q04b

newChile1$F_Q04bn[newChile1$F_Q04b== "1"] = 1
newChile1$F_Q04bn[newChile1$F_Q04b== "2"] = 2
newChile1$F_Q04bn[newChile1$F_Q04b== "3"] = 3
newChile1$F_Q04bn[newChile1$F_Q04b== "4"] = 4
newChile1$F_Q04bn[newChile1$F_Q04b== "5"] = 5
newChile1$F_Q04bn[newChile1$F_Q04b== "N"] = NA

#F_Q05a

newChile1$F_Q05an[newChile1$F_Q05a == "D"] = NA
newChile1$F_Q05an[newChile1$F_Q05a == "N"] = NA
newChile1$F_Q05an[newChile1$F_Q05a == "1"] = 1
newChile1$F_Q05an[newChile1$F_Q05a == "2"] = 2
newChile1$F_Q05an[newChile1$F_Q05a == "3"] = 3
newChile1$F_Q05an[newChile1$F_Q05a == "4"] = 4
newChile1$F_Q05an[newChile1$F_Q05a == "5"] = 5

#F_Q05b

newChile1$F_Q05bn[newChile1$F_Q05b == "D"] = NA
newChile1$F_Q05bn[newChile1$F_Q05b == "N"] = NA
newChile1$F_Q05bn[newChile1$F_Q05b == "1"] = 1
newChile1$F_Q05bn[newChile1$F_Q05b == "2"] = 2
newChile1$F_Q05bn[newChile1$F_Q05b == "3"] = 3
newChile1$F_Q05bn[newChile1$F_Q05b == "4"] = 4
newChile1$F_Q05bn[newChile1$F_Q05b == "5"] = 5

#F_Q07b

newChile1$F_Q07bn[newChile1$F_Q07b == "D"] = NA
newChile1$F_Q07bn[newChile1$F_Q07b == "N"] = NA
newChile1$F_Q07bn[newChile1$F_Q07b == "1"] = 0
newChile1$F_Q07bn[newChile1$F_Q07b == "2"] = 1

# G_Q01a

newChile1$G_Q01an[newChile1$G_Q01a == "N"] = NA
newChile1$G_Q01an[newChile1$G_Q01a == "1"] = 1
newChile1$G_Q01an[newChile1$G_Q01a == "2"] = 2
newChile1$G_Q01an[newChile1$G_Q01a == "3"] = 3
newChile1$G_Q01an[newChile1$G_Q01a == "4"] = 4
newChile1$G_Q01an[newChile1$G_Q01a == "5"] = 5

# G_Q02a

newChile1$G_Q02an[newChile1$G_Q02a == "N"] = NA
newChile1$G_Q02an[newChile1$G_Q02a == "1"] = 1
newChile1$G_Q02an[newChile1$G_Q02a == "2"] = 2
newChile1$G_Q02an[newChile1$G_Q02a == "3"] = 3
newChile1$G_Q02an[newChile1$G_Q02a == "4"] = 4
newChile1$G_Q02an[newChile1$G_Q02a == "5"] = 5

# G_Q02b

newChile1$G_Q02bn[newChile1$G_Q02b== "1"] = 1
newChile1$G_Q02bn[newChile1$G_Q02b== "2"] = 2
newChile1$G_Q02bn[newChile1$G_Q02b== "3"] = 3
newChile1$G_Q02bn[newChile1$G_Q02b== "4"] = 4
newChile1$G_Q02bn[newChile1$G_Q02b== "5"] = 5
newChile1$G_Q02bn[newChile1$G_Q02b== "N"] = NA

# G_Q02c

newChile1$G_Q02cn[newChile1$G_Q02c == "N"] = NA
newChile1$G_Q02cn[newChile1$G_Q02c == "1"] = 1
newChile1$G_Q02cn[newChile1$G_Q02c == "2"] = 2
newChile1$G_Q02cn[newChile1$G_Q02c == "3"] = 3
newChile1$G_Q02cn[newChile1$G_Q02c == "4"] = 4
newChile1$G_Q02cn[newChile1$G_Q02c == "5"] = 5

# G_Q02d

newChile1$G_Q02dn[newChile1$G_Q02d == "N"] = NA
newChile1$G_Q02dn[newChile1$G_Q02d == "1"] = 1
newChile1$G_Q02dn[newChile1$G_Q02d == "2"] = 2
newChile1$G_Q02dn[newChile1$G_Q02d == "3"] = 3
newChile1$G_Q02dn[newChile1$G_Q02d == "4"] = 4
newChile1$G_Q02dn[newChile1$G_Q02d == "5"] = 5

# G_Q03b

newChile1$G_Q03bn[newChile1$G_Q03b == "D"] = NA
newChile1$G_Q03bn[newChile1$G_Q03b == "N"] = NA
newChile1$G_Q03bn[newChile1$G_Q03b == "1"] = 1
newChile1$G_Q03bn[newChile1$G_Q03b == "2"] = 2
newChile1$G_Q03bn[newChile1$G_Q03b == "3"] = 3
newChile1$G_Q03bn[newChile1$G_Q03b == "4"] = 4
newChile1$G_Q03bn[newChile1$G_Q03b == "5"] = 5

# G_Q03c

newChile1$G_Q03cn[newChile1$G_Q03c == "N"] = NA
newChile1$G_Q03cn[newChile1$G_Q03c == "1"] = 1
newChile1$G_Q03cn[newChile1$G_Q03c == "2"] = 2
newChile1$G_Q03cn[newChile1$G_Q03c == "3"] = 3
newChile1$G_Q03cn[newChile1$G_Q03c == "4"] = 4
newChile1$G_Q03cn[newChile1$G_Q03c == "5"] = 5

# G_Q03d

newChile1$G_Q03dn[newChile1$G_Q03d == "N"] = NA
newChile1$G_Q03dn[newChile1$G_Q03d == "1"] = 1
newChile1$G_Q03dn[newChile1$G_Q03d == "2"] = 2
newChile1$G_Q03dn[newChile1$G_Q03d == "3"] = 3
newChile1$G_Q03dn[newChile1$G_Q03d == "4"] = 4
newChile1$G_Q03dn[newChile1$G_Q03d == "5"] = 5

# G_Q03f

newChile1$G_Q03fn[newChile1$G_Q03f == "N"] = NA
newChile1$G_Q03fn[newChile1$G_Q03f == "1"] = 1
newChile1$G_Q03fn[newChile1$G_Q03f == "2"] = 2
newChile1$G_Q03fn[newChile1$G_Q03f == "3"] = 3
newChile1$G_Q03fn[newChile1$G_Q03f == "4"] = 4
newChile1$G_Q03fn[newChile1$G_Q03f == "5"] = 5

# G_Q03g

newChile1$G_Q03gn[newChile1$G_Q03g == "N"] = NA
newChile1$G_Q03gn[newChile1$G_Q03g == "1"] = 1
newChile1$G_Q03gn[newChile1$G_Q03g == "2"] = 2
newChile1$G_Q03gn[newChile1$G_Q03g == "3"] = 3
newChile1$G_Q03gn[newChile1$G_Q03g == "4"] = 4
newChile1$G_Q03gn[newChile1$G_Q03g == "5"] = 5

# G_Q03h

newChile1$G_Q03hn[newChile1$G_Q03h == "N"] = NA
newChile1$G_Q03hn[newChile1$G_Q03h == "1"] = 1
newChile1$G_Q03hn[newChile1$G_Q03h == "2"] = 2
newChile1$G_Q03hn[newChile1$G_Q03h == "3"] = 3
newChile1$G_Q03hn[newChile1$G_Q03h == "4"] = 4
newChile1$G_Q03hn[newChile1$G_Q03h == "5"] = 5

# G_Q04

newChile1$G_Q04n[newChile1$G_Q04 == "N"] = NA
newChile1$G_Q04n[newChile1$G_Q04 == "1"] = 0
newChile1$G_Q04n[newChile1$G_Q04 == "2"] = 1

#G_Q04_T
newChile1$G_Q04_Tn[newEcuador1$G_Q04 == "D"] = NA
newChile1$G_Q04_Tn[newEcuador1$G_Q04 == "V"] = NA
newChile1$G_Q04_Tnn[newEcuador1$G_Q04 == "R"] = NA
newChile1$G_Q04_Tn[newEcuador1$G_Q04 == "N"] = NA
newChile1$G_Q04_Tn[newEcuador1$G_Q04 == "1"] = 1
newChile1$G_Q04_Tn[newEcuador1$G_Q04 == "2"] = 2

# G_Q05a

newChile1$G_Q05an[newChile1$G_Q05a == "V"] = NA
newChile1$G_Q05an[newChile1$G_Q05a == "N"] = NA
newChile1$G_Q05an[newChile1$G_Q05a == "1"] = 1
newChile1$G_Q05an[newChile1$G_Q05a == "2"] = 2
newChile1$G_Q05an[newChile1$G_Q05a == "3"] = 3
newChile1$G_Q05an[newChile1$G_Q05a == "4"] = 4
newChile1$G_Q05an[newChile1$G_Q05a == "5"] = 5

# G_Q05c

newChile1$G_Q05cn[newChile1$G_Q05c == "V"] = NA
newChile1$G_Q05cn[newChile1$G_Q05c == "N"] = NA
newChile1$G_Q05cn[newChile1$G_Q05c == "1"] = 1
newChile1$G_Q05cn[newChile1$G_Q05c == "2"] = 2
newChile1$G_Q05cn[newChile1$G_Q05c == "3"] = 3
newChile1$G_Q05cn[newChile1$G_Q05c == "4"] = 4
newChile1$G_Q05cn[newChile1$G_Q05c == "5"] = 5

#G_Q05d 
newChile1$G_Q05dn[newChile1$G_Q05d == "V"] = NA
newChile1$G_Q05dn[newChile1$G_Q05d == "N"] = NA
newChile1$G_Q05dn[newChile1$G_Q05d == "1"] = 1
newChile1$G_Q05dn[newChile1$G_Q05d == "2"] = 2
newChile1$G_Q05dn[newChile1$G_Q05d == "3"] = 3
newChile1$G_Q05dn[newChile1$G_Q05d == "4"] = 4
newChile1$G_Q05dn[newChile1$G_Q05d == "5"] = 5

#G_Q05e

newChile1$G_Q05en[newChile1$G_Q05e == "V"] = NA
newChile1$G_Q05en[newChile1$G_Q05e == "N"] = NA
newChile1$G_Q05en[newChile1$G_Q05e == "1"] = 1
newChile1$G_Q05en[newChile1$G_Q05e == "2"] = 2
newChile1$G_Q05en[newChile1$G_Q05e == "3"] = 3
newChile1$G_Q05en[newChile1$G_Q05e == "4"] = 4
newChile1$G_Q05en[newChile1$G_Q05e == "5"] = 5

#G_Q05g 

newChile1$G_Q05gn[newChile1$G_Q05g == "V"] = NA
newChile1$G_Q05gn[newChile1$G_Q05g == "N"] = NA
newChile1$G_Q05gn[newChile1$G_Q05g == "1"] = 1
newChile1$G_Q05gn[newChile1$G_Q05g == "2"] = 2
newChile1$G_Q05gn[newChile1$G_Q05g == "3"] = 3
newChile1$G_Q05gn[newChile1$G_Q05g == "4"] = 4
newChile1$G_Q05gn[newChile1$G_Q05g == "5"] = 5

#G_Q05h

newChile1$G_Q05hn[newChile1$G_Q05h == "V"] =NA
newChile1$G_Q05hn[newChile1$G_Q05h == "N"] =NA
newChile1$G_Q05hn[newChile1$G_Q05h == "1"] =1
newChile1$G_Q05hn[newChile1$G_Q05h == "2"] =2
newChile1$G_Q05hn[newChile1$G_Q05h == "3"] =3
newChile1$G_Q05hn[newChile1$G_Q05h == "4"] =4
newChile1$G_Q05hn[newChile1$G_Q05h == "5"] =5


#G_Q06

newChile1$G_Q06n[newChile1$G_Q06 == "V"] =NA
newChile1$G_Q06n[newChile1$G_Q06 == "N"] =NA
newChile1$G_Q06n[newChile1$G_Q06 == "R"] =NA
newChile1$G_Q06n[newChile1$G_Q06 == "1"] =1
newChile1$G_Q06n[newChile1$G_Q06 == "2"] =2
newChile1$G_Q06n[newChile1$G_Q06 == "3"] =3
newChile1$G_Q06n[newChile1$G_Q06 == "4"] =4
newChile1$G_Q06n[newChile1$G_Q06 == "5"] =5

#G_Q07

newChile1$G_Q07n[newChile1$G_Q07 == "V"] =NA
newChile1$G_Q07n[newChile1$G_Q07 == "N"] =NA
newChile1$G_Q07n[newChile1$G_Q07 == "1"] =0
newChile1$G_Q07n[newChile1$G_Q07 == "2"] =1

#G_Q08 

newChile1$G_Q08n[newChile1$G_Q08 == "V"] =NA
newChile1$G_Q08n[newChile1$G_Q08 == "N"] =NA
newChile1$G_Q08n[newChile1$G_Q08 == "D"] =NA
newChile1$G_Q08n[newChile1$G_Q08 == "R"] =NA
newChile1$G_Q08n[newChile1$G_Q08 == "1"] =0
newChile1$G_Q08n[newChile1$G_Q08 == "2"] =1

#H_q01a

newChile1$H_Q01an[newChile1$H_Q01a == "N"] =NA
newChile1$H_Q01an[newChile1$H_Q01a == "1"] =1
newChile1$H_Q01an[newChile1$H_Q01a == "2"] =2
newChile1$H_Q01an[newChile1$H_Q01a == "3"] =3
newChile1$H_Q01an[newChile1$H_Q01a == "4"] =4
newChile1$H_Q01an[newChile1$H_Q01a == "5"] =5

#H_q01b

newChile1$H_Q01bn[newChile1$H_Q01b == "N"] =NA
newChile1$H_Q01bn[newChile1$H_Q01b == "1"] =1
newChile1$H_Q01bn[newChile1$H_Q01b == "2"] =2
newChile1$H_Q01bn[newChile1$H_Q01b == "3"] =3
newChile1$H_Q01bn[newChile1$H_Q01b == "4"] =4
newChile1$H_Q01bn[newChile1$H_Q01b == "5"] =5

#H_q01b_T

newChile1$H_Q01b_Tn[newChile1$H_Q01b_T == "N"] =NA
newChile1$H_Q01b_Tn[newChile1$H_Q01b_T == "1"] =1
newChile1$H_Q01b_Tn[newChile1$H_Q01b_T == "2"] =2
newChile1$H_Q01b_Tn[newChile1$H_Q01b_T == "3"] =3
newChile1$H_Q01b_Tn[newChile1$H_Q01b_T == "4"] =4
newChile1$H_Q01b_Tn[newChile1$H_Q01b_T == "5"] =5

#H_q01c

newChile1$H_Q01cn[newChile1$H_Q01c == "N"] =NA
newChile1$H_Q01cn[newChile1$H_Q01c == "1"] =1
newChile1$H_Q01cn[newChile1$H_Q01c == "2"] =2
newChile1$H_Q01cn[newChile1$H_Q01c == "3"] =3
newChile1$H_Q01cn[newChile1$H_Q01c == "4"] =4
newChile1$H_Q01cn[newChile1$H_Q01c == "5"] =5

#H_q01c_T

newChile1$H_Q01c_Tn[newChile1$H_Q01c_T == "N"] =NA
newChile1$H_Q01c_Tn[newChile1$H_Q01c_T == "1"] =1
newChile1$H_Q01c_Tn[newChile1$H_Q01c_T == "2"] =2
newChile1$H_Q01c_Tn[newChile1$H_Q01c_T == "3"] =3
newChile1$H_Q01c_Tn[newChile1$H_Q01c_T == "4"] =4
newChile1$H_Q01c_Tn[newChile1$H_Q01c_T == "5"] =5

#H_q01d

newChile1$H_Q01dn[newChile1$H_Q01d == "N"] =NA
newChile1$H_Q01dn[newChile1$H_Q01d == "1"] =1
newChile1$H_Q01dn[newChile1$H_Q01d == "2"] =2
newChile1$H_Q01dn[newChile1$H_Q01d == "3"] =3
newChile1$H_Q01dn[newChile1$H_Q01d == "4"] =4
newChile1$H_Q01dn[newChile1$H_Q01d == "5"] =5

#H_q01e

newChile1$H_Q01en[newChile1$H_Q01e == "N"] =NA
newChile1$H_Q01en[newChile1$H_Q01e == "R"] =NA
newChile1$H_Q01en[newChile1$H_Q01e == "1"] =1
newChile1$H_Q01en[newChile1$H_Q01e == "2"] =2
newChile1$H_Q01en[newChile1$H_Q01e == "3"] =3
newChile1$H_Q01en[newChile1$H_Q01e == "4"] =4
newChile1$H_Q01en[newChile1$H_Q01e == "5"] =5

#H_q01e_T

newChile1$H_Q01e_Tn[newChile1$H_Q01e_T == "N"] =NA
newChile1$H_Q01e_Tn[newChile1$H_Q01e_T == "R"] =NA
newChile1$H_Q01e_Tn[newChile1$H_Q01e_T == "1"] =1
newChile1$H_Q01e_Tn[newChile1$H_Q01e_T == "2"] =2
newChile1$H_Q01e_Tn[newChile1$H_Q01e_T == "3"] =3
newChile1$H_Q01e_Tn[newChile1$H_Q01e_T == "4"] =4
newChile1$H_Q01e_Tn[newChile1$H_Q01e_T == "5"] =5

#H_q01f

newChile1$H_Q01fn[newChile1$H_Q01f == "N"] =NA
newChile1$H_Q01fn[newChile1$H_Q01f == "R"] =NA
newChile1$H_Q01fn[newChile1$H_Q01f == "1"] =1
newChile1$H_Q01fn[newChile1$H_Q01f == "2"] =2
newChile1$H_Q01fn[newChile1$H_Q01f == "3"] =3
newChile1$H_Q01fn[newChile1$H_Q01f == "4"] =4
newChile1$H_Q01fn[newChile1$H_Q01f == "5"] =5

#H_q01g

newChile1$H_Q01gn[newChile1$H_Q01g == "N"] =NA
newChile1$H_Q01gn[newChile1$H_Q01g == "1"] =1
newChile1$H_Q01gn[newChile1$H_Q01g == "2"] =2
newChile1$H_Q01gn[newChile1$H_Q01g == "3"] =3
newChile1$H_Q01gn[newChile1$H_Q01g == "4"] =4
newChile1$H_Q01gn[newChile1$H_Q01g == "5"] =5

#H_q01h 

newChile1$H_Q01hn[newChile1$H_Q01h== "1"] = 1
newChile1$H_Q01hn[newChile1$H_Q01h== "2"] = 2
newChile1$H_Q01hn[newChile1$H_Q01h== "3"] = 3
newChile1$H_Q01hn[newChile1$H_Q01h== "4"] = 4
newChile1$H_Q01hn[newChile1$H_Q01h== "5"] = 5
newChile1$H_Q01hn[newChile1$H_Q01h== "N"] = NA

#H_q02a

newChile1$H_Q02an[newChile1$H_Q02a== "1"] = 1
newChile1$H_Q02an[newChile1$H_Q02a== "2"] = 2
newChile1$H_Q02an[newChile1$H_Q02a== "3"] = 3
newChile1$H_Q02an[newChile1$H_Q02a== "4"] = 4
newChile1$H_Q02an[newChile1$H_Q02a== "5"] = 5
newChile1$H_Q02an[newChile1$H_Q02a== "N"] = NA

#H_q02b

newChile1$H_Q02bn[newChile1$H_Q02b== "1"] = 1
newChile1$H_Q02bn[newChile1$H_Q02b== "2"] = 2
newChile1$H_Q02bn[newChile1$H_Q02b== "3"] = 3
newChile1$H_Q02bn[newChile1$H_Q02b== "4"] = 4
newChile1$H_Q02bn[newChile1$H_Q02b== "5"] = 5
newChile1$H_Q02bn[newChile1$H_Q02b== "N"] = NA

#H_q02c

newChile1$H_Q02cn[newChile1$H_Q02c== "1"] = 1
newChile1$H_Q02cn[newChile1$H_Q02c== "2"] = 2
newChile1$H_Q02cn[newChile1$H_Q02c== "3"] = 3
newChile1$H_Q02cn[newChile1$H_Q02c== "4"] = 4
newChile1$H_Q02cn[newChile1$H_Q02c== "5"] = 5
newChile1$H_Q02cn[newChile1$H_Q02c== "N"] = NA

#H_q02d

newChile1$H_Q02dn[newChile1$H_Q02d== "1"] = 1
newChile1$H_Q02dn[newChile1$H_Q02d== "2"] = 2
newChile1$H_Q02dn[newChile1$H_Q02d== "3"] = 3
newChile1$H_Q02dn[newChile1$H_Q02d== "4"] = 4
newChile1$H_Q02dn[newChile1$H_Q02d== "5"] = 5
newChile1$H_Q02dn[newChile1$H_Q02d== "N"] = NA

#H_q03b

newChile1$H_Q03bn[newChile1$H_Q03b== "1"] = 1
newChile1$H_Q03bn[newChile1$H_Q03b== "2"] = 2
newChile1$H_Q03bn[newChile1$H_Q03b== "3"] = 3
newChile1$H_Q03bn[newChile1$H_Q03b== "4"] = 4
newChile1$H_Q03bn[newChile1$H_Q03b== "5"] = 5
newChile1$H_Q03bn[newChile1$H_Q03b== "N"] = NA

#H_q03c

newChile1$H_Q03cn[newChile1$H_Q03c== "1"] = 1
newChile1$H_Q03cn[newChile1$H_Q03c== "2"] = 2
newChile1$H_Q03cn[newChile1$H_Q03c== "3"] = 3
newChile1$H_Q03cn[newChile1$H_Q03c== "4"] = 4
newChile1$H_Q03cn[newChile1$H_Q03c== "5"] = 5
newChile1$H_Q03cn[newChile1$H_Q03c== "D"] = NA
newChile1$H_Q03cn[newChile1$H_Q03c== "N"] = NA

#H_q03d

newChile1$H_Q03dn[newChile1$H_Q03d== "1"] = 1
newChile1$H_Q03dn[newChile1$H_Q03d== "2"] = 2
newChile1$H_Q03dn[newChile1$H_Q03d== "3"] = 3
newChile1$H_Q03dn[newChile1$H_Q03d== "4"] = 4
newChile1$H_Q03dn[newChile1$H_Q03d== "5"] = 5
newChile1$H_Q03dn[newChile1$H_Q03d== "N"] = NA

#H_q03f

newChile1$H_Q03fn[newChile1$H_Q03f== "1"] = 1
newChile1$H_Q03fn[newChile1$H_Q03f== "2"] = 2
newChile1$H_Q03fn[newChile1$H_Q03f== "3"] = 3
newChile1$H_Q03fn[newChile1$H_Q03f== "4"] = 4
newChile1$H_Q03fn[newChile1$H_Q03f== "5"] = 5
newChile1$H_Q03fn[newChile1$H_Q03f== "N"] = NA

#H_q03g

newChile1$H_Q03gn[newChile1$H_Q03g== "1"] = 1
newChile1$H_Q03gn[newChile1$H_Q03g== "2"] = 2
newChile1$H_Q03gn[newChile1$H_Q03g== "3"] = 3
newChile1$H_Q03gn[newChile1$H_Q03g== "4"] = 4
newChile1$H_Q03gn[newChile1$H_Q03g== "5"] = 5
newChile1$H_Q03gn[newChile1$H_Q03g== "N"] = NA

#H_q03h

newChile1$H_Q03hn[newChile1$H_Q03h== "1"] = 1
newChile1$H_Q03hn[newChile1$H_Q03h== "2"] = 2
newChile1$H_Q03hn[newChile1$H_Q03h== "3"] = 3
newChile1$H_Q03hn[newChile1$H_Q03h== "4"] = 4
newChile1$H_Q03hn[newChile1$H_Q03h== "5"] = 5
newChile1$H_Q03hn[newChile1$H_Q03h== "N"] = NA

#H_Q04a

newChile1$H_Q04an[newChile1$H_Q04a == "V"] =NA
newChile1$H_Q04an[newChile1$H_Q04a == "N"] =NA
newChile1$H_Q04an[newChile1$H_Q04a == "1"] =0
newChile1$H_Q04an[newChile1$H_Q04a == "2"] =1

#H_Q04b

newChile1$H_Q04bn[newChile1$H_Q04b == "V"] =NA
newChile1$H_Q04bn[newChile1$H_Q04b == "N"] =NA
newChile1$H_Q04bn[newChile1$H_Q04b == "1"] =0
newChile1$H_Q04bn[newChile1$H_Q04b == "2"] =1

#H_Q05a

newChile1$H_Q05an[newChile1$H_Q05a == "V"] =NA
newChile1$H_Q05an[newChile1$H_Q05a == "N"] =NA
newChile1$H_Q05an[newChile1$H_Q05a == "1"] =1
newChile1$H_Q05an[newChile1$H_Q05a == "2"] =2
newChile1$H_Q05an[newChile1$H_Q05a == "3"] =3
newChile1$H_Q05an[newChile1$H_Q05a == "4"] =4
newChile1$H_Q05an[newChile1$H_Q05a == "5"] =5

#H_Q05c

newChile1$H_Q05cn[newChile1$H_Q05c == "V"] =NA
newChile1$H_Q05cn[newChile1$H_Q05c == "N"] =NA
newChile1$H_Q05cn[newChile1$H_Q05c == "1"] =1
newChile1$H_Q05cn[newChile1$H_Q05c == "2"] =2
newChile1$H_Q05cn[newChile1$H_Q05c == "3"] =3
newChile1$H_Q05cn[newChile1$H_Q05c == "4"] =4
newChile1$H_Q05cn[newChile1$H_Q05c == "5"] =5

#H_Q05d

newChile1$H_Q05dn[newChile1$H_Q05d == "V"] =NA
newChile1$H_Q05dn[newChile1$H_Q05d == "N"] =NA
newChile1$H_Q05dn[newChile1$H_Q05d == "1"] =1
newChile1$H_Q05dn[newChile1$H_Q05d == "2"] =2
newChile1$H_Q05dn[newChile1$H_Q05d == "3"] =3
newChile1$H_Q05dn[newChile1$H_Q05d == "4"] =4
newChile1$H_Q05dn[newChile1$H_Q05d == "5"] =5

#H_Q05e

newChile1$H_Q05en[newChile1$H_Q05e == "V"] =NA
newChile1$H_Q05en[newChile1$H_Q05e == "N"] =NA
newChile1$H_Q05en[newChile1$H_Q05e == "1"] =1
newChile1$H_Q05en[newChile1$H_Q05e == "2"] =2
newChile1$H_Q05en[newChile1$H_Q05e == "3"] =3
newChile1$H_Q05en[newChile1$H_Q05e == "4"] =4
newChile1$H_Q05en[newChile1$H_Q05e == "5"] =5

#H_Q05f

newChile1$H_Q05fn[newChile1$H_Q05f == "V"] =NA
newChile1$H_Q05fn[newChile1$H_Q05f == "N"] =NA
newChile1$H_Q05fn[newChile1$H_Q05f == "1"] =1
newChile1$H_Q05fn[newChile1$H_Q05f == "2"] =2
newChile1$H_Q05fn[newChile1$H_Q05f == "3"] =3
newChile1$H_Q05fn[newChile1$H_Q05f == "4"] =4
newChile1$H_Q05fn[newChile1$H_Q05f == "5"] =5

#H_Q05g

newChile1$H_Q05gn[newChile1$H_Q05g == "V"] =NA
newChile1$H_Q05gn[newChile1$H_Q05g == "N"] =NA
newChile1$H_Q05gn[newChile1$H_Q05g == "1"] =1
newChile1$H_Q05gn[newChile1$H_Q05g == "2"] =2
newChile1$H_Q05gn[newChile1$H_Q05g == "3"] =3
newChile1$H_Q05gn[newChile1$H_Q05g == "4"] =4
newChile1$H_Q05gn[newChile1$H_Q05g == "5"] =5

#H_Q05h

newChile1$H_Q05hn[newChile1$H_Q05h == "V"] =NA
newChile1$H_Q05hn[newChile1$H_Q05h == "N"] =NA
newChile1$H_Q05hn[newChile1$H_Q05h == "1"] =1
newChile1$H_Q05hn[newChile1$H_Q05h == "2"] =2
newChile1$H_Q05hn[newChile1$H_Q05h == "3"] =3
newChile1$H_Q05hn[newChile1$H_Q05h == "4"] =4
newChile1$H_Q05hn[newChile1$H_Q05h == "5"] =5

#J_Q03a

newChile1$J_Q03an[newChile1$J_Q03a == "N"] = NA
newChile1$J_Q03an[newChile1$J_Q03a == "1"] = 0
newChile1$J_Q03an[newChile1$J_Q03a == "2"] = 1

#J_Q03b

newChile1$J_Q03bn[newChile1$J_Q03b == "N"] = NA
newChile1$J_Q03bn[newChile1$J_Q03b == "R"] = NA
newChile1$J_Q03bn[newChile1$J_Q03b == "V"] = NA
newChile1$J_Q03bn[newChile1$J_Q03b == "1"] = 1
newChile1$J_Q03bn[newChile1$J_Q03b == "2"] = 2
newChile1$J_Q03bn[newChile1$J_Q03b == "3"] = 3
newChile1$J_Q03bn[newChile1$J_Q03b == "4"] = 4
newChile1$J_Q03bn[newChile1$J_Q03b == "5"] = 5
newChile1$J_Q03bn[newChile1$J_Q03b == "6"] = 6
newChile1$J_Q03bn[newChile1$J_Q03b == "7"] = 7
newChile1$J_Q03bn[newChile1$J_Q03b == "8"] = 8
newChile1$J_Q03bn[newChile1$J_Q03b == "9"] = 9
newChile1$J_Q03bn[newChile1$J_Q03b == "10"] = 10
newChile1$J_Q03bn[newChile1$J_Q03b == "11"] = 11
newChile1$J_Q03bn[newChile1$J_Q03b == "12"] = 12
newChile1$J_Q03bn[newChile1$J_Q03b == "13"] = 13
newChile1$J_Q03bn[newChile1$J_Q03b == "16"] = 16
newChile1$J_Q03bn[newChile1$J_Q03b == "19"] = 19

#J_Q06b

newChile1$J_Q06bn[newChile1$J_Q06b== "1"] = 1
newChile1$J_Q06bn[newChile1$J_Q06b== "2"] = 2
newChile1$J_Q06bn[newChile1$J_Q06b== "3"] = 3
newChile1$J_Q06bn[newChile1$J_Q06b== "D"] = NA
newChile1$J_Q06bn[newChile1$J_Q06b== "N"] = NA
newChile1$J_Q06bn[newChile1$J_Q06b== "R"] = NA

#J_Q07b

newChile1$J_Q07bn[newChile1$J_Q07b== "1"] = 1
newChile1$J_Q07bn[newChile1$J_Q07b== "2"] = 2
newChile1$J_Q07bn[newChile1$J_Q07b== "3"] = 3
newChile1$J_Q07bn[newChile1$J_Q07b== "D"] = NA
newChile1$J_Q07bn[newChile1$J_Q07b== "N"] = NA
newChile1$J_Q07bn[newChile1$J_Q07b== "R"] = NA


```


<br>

**Dropping NAs**


<br>

