---
title: "Peru"
author: "Luisa Olaya"
date: "3/2/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
set.seed(42) #for consistent results
library(haven)
library(foreign)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stargazer)
library(naniar)
library(car)
library(carData)
library(FactoMineR)
library(factoextra)

#Peru <- read.csv("/Users/lu/Dropbox/Hertie/3/Thesis/R/prgperp1.csv")
Peru <- read.csv("/Users/lu/Dropbox/Hertie/3/Thesis/Thesis-/ThesisPeru.Rmd")
```


<br>

**First steps: preparing the data **

1. Selection of variables per group of skills ICT, Numeracy and Literacy

2. Identification of NAs in the possible independent variables (all those that signal income) for this the explored variables were YEARLYINCPR, EARNMTHPPP, EARNHR, EARNHRBONUS, EARNHRBONUSPPP. What we found was that almost all of them have at least 2847 NAs or V that stands in the data ser for valid skip. Thus, taking into account that this is the most important variable of our study we reduced the data set to the number of observations that reported something in the variable MONTHLYINCPR, which reduces our data set from 6289 observations to 4826. 

3. More over we analyed the number of NAs or V in the other variables selected. The main findings were that ICT skills are the ones with more missings. 
--> For ICT skills in work they have 3130 Vs  and 2 Ns out of 4826 observations. 
--> For ICT skills in daily life 2465 Vs and 3 Ns out of 4826 observations. 

--> However more general questions about the use of computer and whose answers were limited to (yes/no) such as computer COMPUTEREXPERIENCE had only 8 NAs and no Vs

--> Computer experience in job G_Q04 registered only 2 Ns and same for G_Q04_T

--> Computer experience in daily life H_Q04a registered 1694 V and H_Q04b 1425 V and 3 Ns


<br>

###Subsetting the data 

```{r cars}

newPeru <- Peru %>% 
  select("AGE_R", "GENDER_R","B_Q01a", "B_Q01a_T", "B_Q02a", "B_Q02c", "B_Q10c", "B_Q01b", "C_Q01a", "C_Q01c", "C_Q02a", "D_Q03", "D_Q14", "D_Q16a", "D_Q18a_T", "F_Q01b","F_Q02b","F_Q02c","F_Q02d","F_Q02e","F_Q03b","F_Q04a","F_Q04b","F_Q05a","F_Q05b","F_Q07b","G_Q01a","G_Q02a","G_Q02b","G_Q02c","G_Q02d","G_Q03b","G_Q03c","G_Q03d","G_Q03f","G_Q03g","G_Q03h", "G_Q04", "G_Q04_T", "G_Q05a", "G_Q05c", "G_Q05d", "G_Q05e", "G_Q05g", "G_Q05h", "G_Q06", "G_Q07", "G_Q08", "H_Q01a", "H_Q01b", "H_Q01b_T", "H_Q01c", "H_Q01c_T", "H_Q01d", "H_Q01e", "H_Q01e_T", "H_Q01f", "H_Q01g", "H_Q01h", "H_Q02a", "H_Q02b","H_Q02c", "H_Q02d", "H_Q03b", "H_Q03c", "H_Q03d", "H_Q03f", "H_Q03g", "H_Q03h","H_Q04a", "H_Q04b", "H_Q05a", "H_Q05c", "H_Q05d", "H_Q05e", "H_Q05f", "H_Q05g", "H_Q05h", "J_Q03a", "J_Q03b", "J_Q06b", "J_Q07b","COMPUTEREXPERIENCE", "MONTHLYINCPR","YEARLYINCPR", "REG_TL2")

gg_miss_var(newPeru)


table(is.na(newPeru$YEARLYINCPR))

table(is.na(newPeru$MONTHLYINCPR))

#droping NAs from the independent variable 


newPeru1 <- drop_na(newPeru, MONTHLYINCPR)

# Number of women and men 


barplot(table(newPeru1$GENDER_R))
newPeru1 %>% count(GENDER_R)

# Education status
newPeru1 %>% count(B_Q01a)
newPeru1 %>% count(B_Q01a_T)
newPeru1 %>% count(B_Q02a)
newPeru1 %>% count(B_Q02c) #x - 3224 V ESTA 1
newPeru1 %>% count(B_Q10c) #x- 3176 V ESTA 2
newPeru1 %>% count(B_Q01b) # 2134 v ESTA 3

# Work status 
newPeru1 %>% count(C_Q01a)
newPeru1 %>% count(C_Q01c) # 3459 v ESTA 4
newPeru1 %>% count(C_Q02a) # 3459 v ESTA 5 
newPeru1 %>% count(D_Q03) # D 42 - r21 
newPeru1 %>% count(D_Q14) #
newPeru1 %>% count(D_Q16a) # V 1008
newPeru1 %>% count(D_Q18a_T) # 13 NA 


# ICT skills in Job
newPeru1 %>% count(G_Q04) # experience with computer in job yes no  2n
newPeru1%>% count(G_Q04_T) #** 2N
newPeru1 %>% count(COMPUTEREXPERIENCE) # 8Nas
newPeru1 %>% count(G_Q05a) # 3130  + N 2
newPeru1 %>% count(G_Q05c) # 3130  + N 2
newPeru1 %>% count(G_Q05d) # 3130  + N 2
newPeru1 %>% count(G_Q05e) # 3130  + N 2
newPeru1 %>% count(G_Q05g) # 3130  + N 2
newPeru1 %>% count(G_Q05h) # 3130  + N 2 
newPeru1 %>% count(G_Q06) # 3130  + N 2
newPeru1 %>% count(G_Q07) # 3130  + N 2
newPeru1 %>% count(G_Q08) # 3130  + N 2

#ICT skills in daily life
newPeru1 %>% count(H_Q04a) # 1694 V + 3 Ns experience with compiuter every life
newPeru1 %>% count(H_Q04b) # 1425 V + 3 Ns
newPeru1 %>% count(H_Q05a) # 2465 + 3 ns  
newPeru1 %>% count(H_Q05c) # 2465 + 3 ns 
newPeru1 %>% count(H_Q05d) # 2465 + 3 ns 
newPeru1 %>% count(H_Q05e) # 2465 + 3 ns
newPeru1 %>% count(H_Q05f) # 2465 + 3 ns
newPeru1 %>% count(H_Q05g) # 2465 + 3 ns
newPeru1 %>% count(H_Q05h) # 2465 + 3 ns 

# Children and parents level of education
newPeru1 %>% count(J_Q03a)
newPeru1 %>% count(J_Q03b) #943
newPeru1 %>% count(J_Q06b) 

# Soft skills 
newPeru1 %>% count(F_Q01b) #748
newPeru1 %>% count(F_Q02b) 
newPeru1 %>% count(F_Q02c)
newPeru1 %>% count(F_Q02d)
newPeru1 %>% count(F_Q02e)
newPeru1 %>% count(F_Q03b)
newPeru1 %>% count(F_Q04a)
newPeru1 %>% count(F_Q04b)
newPeru1 %>% count(F_Q05a)
newPeru1 %>% count(F_Q05b)

# Literacy work 
newPeru1 %>% count(G_Q01a)
newPeru1 %>% count(G_Q02a)
newPeru1 %>% count(G_Q02b)
newPeru1 %>% count(G_Q02c)
newPeru1 %>% count(G_Q02d)

# Numeracy work 
newPeru1 %>% count(G_Q03b)
newPeru1 %>% count(G_Q03c)
newPeru1 %>% count(G_Q03d)
newPeru1 %>% count(G_Q03f)
newPeru1 %>% count(G_Q03g)
newPeru1 %>% count(G_Q03h)

# Literacy life
newPeru1 %>% count(H_Q01a)
newPeru1 %>% count(H_Q01b)
newPeru1 %>% count(H_Q01b_T)
newPeru1 %>% count(H_Q01d)
newPeru1 %>% count(H_Q01c)
newPeru1 %>% count(H_Q01e)
newPeru1 %>% count(H_Q01e_T)
newPeru1 %>% count(H_Q01f)
newPeru1 %>% count(H_Q01g)
newPeru1 %>% count(H_Q01h)
newPeru1 %>% count(H_Q02a)
newPeru1 %>% count(H_Q02b)
newPeru1 %>% count(H_Q02c)
newPeru1 %>% count(H_Q02d)

# Numeracy life
newPeru1 %>% count(H_Q03b)
newPeru1 %>% count(H_Q03c)
newPeru1 %>% count(H_Q03d)
newPeru1 %>% count(H_Q03f)
newPeru1 %>% count(H_Q03g)
newPeru1 %>% count(H_Q03h)

# Region
newPeru1 %>% count(REG_TL2)

## Income variables
Peru %>% count(YEARLYINCPR) #2464 NAs
Peru %>% count(EARNMTH) # N 2550 v 4627
Peru %>% count(EARNMTHPPP) # 2550 v 4627
Peru %>% count(EARNHR) ## N 2550 v 4627
Peru %>% count(EARNHRBONUS) # # N 2550 v 4627
Peru %>% count(ICTWORK) # N 2550 v 4627
Peru %>% count(EARNHRBONUSPPP) # # N 2550 v 4627
Peru %>% count(EARNFLAG) # N 2550 v 4627


```

<br>

**Adaptation of the dataset **

Since there are non numeric factor in our dataset such as V, N and R we had to convert them in NAs in order to work with thw variables afterwards. 

<br>

```{r pressure, echo=FALSE}
#Gender

newPeru1$GENDER_Rn[newPeru1$GENDER_R == "1"] = 0
newPeru1$GENDER_Rn[newPeru1$GENDER_R == "2"] = 1


#B_Q01a
newPeru1$B_Q01an[newPeru1$B_Q01a == "D"] = NA
newPeru1$B_Q01an[newPeru1$B_Q01a == "1"] = 1
newPeru1$B_Q01an[newPeru1$B_Q01a == "2"] = 2
newPeru1$B_Q01an[newPeru1$B_Q01a == "5"] = 5 
newPeru1$B_Q01an[newPeru1$B_Q01a == "6"] = 6
newPeru1$B_Q01an[newPeru1$B_Q01a == "7"] = 7
newPeru1$B_Q01an[newPeru1$B_Q01a == "11"] = 11
newPeru1$B_Q01an[newPeru1$B_Q01a == "12"] = 12
newPeru1$B_Q01an[newPeru1$B_Q01a == "13"] = 13
newPeru1$B_Q01an[newPeru1$B_Q01a == "14"] = 14
newPeru1$B_Q01an[newPeru1$B_Q01a == "15"] = 15

#B_Q01a_T

newPeru1$B_Q01a_Tn[newPeru1$B_Q01a_T == "M"] = NA
newPeru1$B_Q01a_Tn[newPeru1$B_Q01a_T == "1"] = 1
newPeru1$B_Q01a_Tn[newPeru1$B_Q01a_T == "2"] = 2
newPeru1$B_Q01a_Tn[newPeru1$B_Q01a_T == "3"] = 3 
newPeru1$B_Q01a_Tn[newPeru1$B_Q01a_T == "4"] = 4

#B_Q02a

newPeru1$B_Q02an[newPeru1$B_Q02a == "R"] = NA
newPeru1$B_Q02an[newPeru1$B_Q02a == "1"] = 0
newPeru1$B_Q02an[newPeru1$B_Q02a== "2"] = 1

#B_Q02c
newPeru1$B_Q02cn[newPeru1$B_Q02c == "V"] = NA
newPeru1$B_Q02cn[newPeru1$B_Q02c == "1"] = 1
newPeru1$B_Q02cn[newPeru1$B_Q02c == "2"] = 2
newPeru1$B_Q02cn[newPeru1$B_Q02c == "3"] = 3
newPeru1$B_Q02cn[newPeru1$B_Q02c == "4"] = 4
newPeru1$B_Q02cn[newPeru1$B_Q02c == "5"] = 5
newPeru1$B_Q02cn[newPeru1$B_Q02c == "6"] = 6
newPeru1$B_Q02cn[newPeru1$B_Q02c == "7"] = 7
newPeru1$B_Q02cn[newPeru1$B_Q02c == "8"] = 8
newPeru1$B_Q02cn[newPeru1$B_Q02c == "9"] = 9 
newPeru1$B_Q02cn[newPeru1$B_Q02c == "R"] = NA

#B_Q10c

newPeru1$B_Q10cn[newPeru1$B_Q10c == "V"] = NA
newPeru1$B_Q10cn[newPeru1$B_Q10c == "1"] = 1
newPeru1$B_Q10cn[newPeru1$B_Q10c == "2"] = 2
newPeru1$B_Q10cn[newPeru1$B_Q10c == "3"] = 3
newPeru1$B_Q10cn[newPeru1$B_Q10c == "4"] = 4

#B_Q01b

newPeru1$B_Q01bn[newPeru1$B_Q01b == "V"] = NA
newPeru1$B_Q01bn[newPeru1$B_Q01b == "D"] = NA
newPeru1$B_Q01bn[newPeru1$B_Q01b == "R"] = NA
newPeru1$B_Q01bn[newPeru1$B_Q01b == "1"] = 1
newPeru1$B_Q01bn[newPeru1$B_Q01b == "2"] = 2
newPeru1$B_Q01bn[newPeru1$B_Q01b == "3"] = 3
newPeru1$B_Q01bn[newPeru1$B_Q01b == "4"] = 4
newPeru1$B_Q01bn[newPeru1$B_Q01b == "5"] = 5
newPeru1$B_Q01bn[newPeru1$B_Q01b == "6"] = 6
newPeru1$B_Q01bn[newPeru1$B_Q01b == "7"] = 7
newPeru1$B_Q01bn[newPeru1$B_Q01b == "8"] = 8
newPeru1$B_Q01bn[newPeru1$B_Q01b == "9"] = 9

#C_Q01a
newPeru1$C_Q01an[newPeru1$C_Q01a == "N"] = NA

# C_Q01c
newPeru1$C_Q01cn[newPeru1$C_Q01c == "V"] = NA

#C_Q02a

newPeru1$C_Q02an[newPeru1$C_Q02a == "V"] = NA

#D_Q03

newPeru1$D_Q03n[newPeru1$D_Q03 == "R"] = NA
newPeru1$D_Q03n[newPeru1$D_Q03 == "D"] = NA
newPeru1$D_Q03n[newPeru1$D_Q03 == "1"] = 1
newPeru1$D_Q03n[newPeru1$D_Q03 == "2"] = 2
newPeru1$D_Q03n[newPeru1$D_Q03 == "3"] = 3




#D_Q14

newPeru1$D_Q14n[newPeru1$D_Q14 == "D"] = NA
newPeru1$D_Q14n[newPeru1$D_Q14 == "1"] = 1
newPeru1$D_Q14n[newPeru1$D_Q14 == "2"] = 2
newPeru1$D_Q14n[newPeru1$D_Q14 == "3"] = 3
newPeru1$D_Q14n[newPeru1$D_Q14 == "4"] = 4
newPeru1$D_Q14n[newPeru1$D_Q14 == "5"] = 5

#D_Q16a

newPeru1$D_Q16an[newPeru1$D_Q16a == "V"] = NA
newPeru1$D_Q16an[newPeru1$D_Q16a == "1"] = 1
newPeru1$D_Q16an[newPeru1$D_Q16a == "2"] = 2
newPeru1$D_Q16an[newPeru1$D_Q16a == "3"] = 3
newPeru1$D_Q16an[newPeru1$D_Q16a == "4"] = 4
newPeru1$D_Q16an[newPeru1$D_Q16a == "5"] = 5
newPeru1$D_Q16an[newPeru1$D_Q16a == "6"] = 6
newPeru1$D_Q16an[newPeru1$D_Q16a == "7"] = 7

#F_Q01b

newPeru1$F_Q01bn[newPeru1$F_Q01b== "1"] = 1
newPeru1$F_Q01bn[newPeru1$F_Q01b== "2"] = 2
newPeru1$F_Q01bn[newPeru1$F_Q01b== "3"] = 3
newPeru1$F_Q01bn[newPeru1$F_Q01b== "4"] = 4
newPeru1$F_Q01bn[newPeru1$F_Q01b== "5"] = 5
newPeru1$F_Q01bn[newPeru1$F_Q01b== "N"] = NA
newPeru1$F_Q01bn[newPeru1$F_Q01b== "R"] = NA
newPeru1$F_Q01bn[newPeru1$F_Q01b== "V"] = NA

#F_Q02b

newPeru1$F_Q02bn[newPeru1$F_Q02b== "1"] = 1
newPeru1$F_Q02bn[newPeru1$F_Q02b== "2"] = 2
newPeru1$F_Q02bn[newPeru1$F_Q02b== "3"] = 3
newPeru1$F_Q02bn[newPeru1$F_Q02b== "4"] = 4
newPeru1$F_Q02bn[newPeru1$F_Q02b== "5"] = 5
newPeru1$F_Q02bn[newPeru1$F_Q02b== "N"] = NA
newPeru1$F_Q02bn[newPeru1$F_Q02b== "R"] = NA

#F_Q02c

newPeru1$F_Q02cn[newPeru1$F_Q02c== "1"] = 1
newPeru1$F_Q02cn[newPeru1$F_Q02c== "2"] = 2
newPeru1$F_Q02cn[newPeru1$F_Q02c== "3"] = 3
newPeru1$F_Q02cn[newPeru1$F_Q02c== "4"] = 4
newPeru1$F_Q02cn[newPeru1$F_Q02c== "5"] = 5
newPeru1$F_Q02cn[newPeru1$F_Q02c== "N"] = NA
newPeru1$F_Q02cn[newPeru1$F_Q02c== "R"] = NA

#F_Q02d

newPeru1$F_Q02dn[newPeru1$F_Q02d== "1"] = 1
newPeru1$F_Q02dn[newPeru1$F_Q02d== "2"] = 2
newPeru1$F_Q02dn[newPeru1$F_Q02d== "3"] = 3
newPeru1$F_Q02dn[newPeru1$F_Q02d== "4"] = 4
newPeru1$F_Q02dn[newPeru1$F_Q02d== "5"] = 5
newPeru1$F_Q02dn[newPeru1$F_Q02d== "D"] = NA
newPeru1$F_Q02dn[newPeru1$F_Q02d== "N"] = NA 
newPeru1$F_Q02dn[newPeru1$F_Q02d== "R"] = NA

#F_Q02e

newPeru1$F_Q02en[newPeru1$F_Q02e== "1"] = 1
newPeru1$F_Q02en[newPeru1$F_Q02e== "2"] = 2
newPeru1$F_Q02en[newPeru1$F_Q02e== "3"] = 3
newPeru1$F_Q02en[newPeru1$F_Q02e== "4"] = 4
newPeru1$F_Q02en[newPeru1$F_Q02e== "5"] = 5
newPeru1$F_Q02en[newPeru1$F_Q02e== "N"] = NA 
newPeru1$F_Q02en[newPeru1$F_Q02e== "R"] = NA

#F_Q03b

newPeru1$F_Q03bn[newPeru1$F_Q03b== "1"] = 1
newPeru1$F_Q03bn[newPeru1$F_Q03b== "2"] = 2
newPeru1$F_Q03bn[newPeru1$F_Q03b== "3"] = 3
newPeru1$F_Q03bn[newPeru1$F_Q03b== "4"] = 4
newPeru1$F_Q03bn[newPeru1$F_Q03b== "5"] = 5
newPeru1$F_Q03bn[newPeru1$F_Q03b== "D"] = NA
newPeru1$F_Q03bn[newPeru1$F_Q03b== "N"] = NA

#F_Q04a

newPeru1$F_Q04an[newPeru1$F_Q04a== "1"] = 1
newPeru1$F_Q04an[newPeru1$F_Q04a== "2"] = 2
newPeru1$F_Q04an[newPeru1$F_Q04a== "3"] = 3
newPeru1$F_Q04an[newPeru1$F_Q04a== "4"] = 4
newPeru1$F_Q04an[newPeru1$F_Q04a== "5"] = 5
newPeru1$F_Q04an[newPeru1$F_Q04a== "D"] = NA
newPeru1$F_Q04an[newPeru1$F_Q04a== "N"] = NA

#F_Q04b

newPeru1$F_Q04bn[newPeru1$F_Q04b== "1"] = 1
newPeru1$F_Q04bn[newPeru1$F_Q04b== "2"] = 2
newPeru1$F_Q04bn[newPeru1$F_Q04b== "3"] = 3
newPeru1$F_Q04bn[newPeru1$F_Q04b== "4"] = 4
newPeru1$F_Q04bn[newPeru1$F_Q04b== "5"] = 5
newPeru1$F_Q04bn[newPeru1$F_Q04b== "N"] = NA

#F_Q05a

newPeru1$F_Q05an[newPeru1$F_Q05a == "D"] = NA
newPeru1$F_Q05an[newPeru1$F_Q05a == "N"] = NA
newPeru1$F_Q05an[newPeru1$F_Q05a == "1"] = 1
newPeru1$F_Q05an[newPeru1$F_Q05a == "2"] = 2
newPeru1$F_Q05an[newPeru1$F_Q05a == "3"] = 3
newPeru1$F_Q05an[newPeru1$F_Q05a == "4"] = 4
newPeru1$F_Q05an[newPeru1$F_Q05a == "5"] = 5

#F_Q05b

newPeru1$F_Q05bn[newPeru1$F_Q05b == "D"] = NA
newPeru1$F_Q05bn[newPeru1$F_Q05b == "N"] = NA
newPeru1$F_Q05bn[newPeru1$F_Q05b == "1"] = 1
newPeru1$F_Q05bn[newPeru1$F_Q05b == "2"] = 2
newPeru1$F_Q05bn[newPeru1$F_Q05b == "3"] = 3
newPeru1$F_Q05bn[newPeru1$F_Q05b == "4"] = 4
newPeru1$F_Q05bn[newPeru1$F_Q05b == "5"] = 5

#F_Q07b

newPeru1$F_Q07bn[newPeru1$F_Q07b == "D"] = NA
newPeru1$F_Q07bn[newPeru1$F_Q07b == "N"] = NA
newPeru1$F_Q07bn[newPeru1$F_Q07b == "1"] = 0
newPeru1$F_Q07bn[newPeru1$F_Q07b == "2"] = 1

# G_Q01a

newPeru1$G_Q01an[newPeru1$G_Q01a == "N"] = NA
newPeru1$G_Q01an[newPeru1$G_Q01a == "1"] = 1
newPeru1$G_Q01an[newPeru1$G_Q01a == "2"] = 2
newPeru1$G_Q01an[newPeru1$G_Q01a == "3"] = 3
newPeru1$G_Q01an[newPeru1$G_Q01a == "4"] = 4
newPeru1$G_Q01an[newPeru1$G_Q01a == "5"] = 5

# G_Q02a

newPeru1$G_Q02an[newPeru1$G_Q02a == "N"] = NA
newPeru1$G_Q02an[newPeru1$G_Q02a == "1"] = 1
newPeru1$G_Q02an[newPeru1$G_Q02a == "2"] = 2
newPeru1$G_Q02an[newPeru1$G_Q02a == "3"] = 3
newPeru1$G_Q02an[newPeru1$G_Q02a == "4"] = 4
newPeru1$G_Q02an[newPeru1$G_Q02a == "5"] = 5

# G_Q02b

newPeru1$G_Q02bn[newPeru1$G_Q02b== "1"] = 1
newPeru1$G_Q02bn[newPeru1$G_Q02b== "2"] = 2
newPeru1$G_Q02bn[newPeru1$G_Q02b== "3"] = 3
newPeru1$G_Q02bn[newPeru1$G_Q02b== "4"] = 4
newPeru1$G_Q02bn[newPeru1$G_Q02b== "5"] = 5
newPeru1$G_Q02bn[newPeru1$G_Q02b== "N"] = NA

# G_Q02c

newPeru1$G_Q02cn[newPeru1$G_Q02c == "N"] = NA
newPeru1$G_Q02cn[newPeru1$G_Q02c == "1"] = 1
newPeru1$G_Q02cn[newPeru1$G_Q02c == "2"] = 2
newPeru1$G_Q02cn[newPeru1$G_Q02c == "3"] = 3
newPeru1$G_Q02cn[newPeru1$G_Q02c == "4"] = 4
newPeru1$G_Q02cn[newPeru1$G_Q02c == "5"] = 5

# G_Q02d

newPeru1$G_Q02dn[newPeru1$G_Q02d == "N"] = NA
newPeru1$G_Q02dn[newPeru1$G_Q02d == "1"] = 1
newPeru1$G_Q02dn[newPeru1$G_Q02d == "2"] = 2
newPeru1$G_Q02dn[newPeru1$G_Q02d == "3"] = 3
newPeru1$G_Q02dn[newPeru1$G_Q02d == "4"] = 4
newPeru1$G_Q02dn[newPeru1$G_Q02d == "5"] = 5

# G_Q03b

newPeru1$G_Q03bn[newPeru1$G_Q03b == "D"] = NA
newPeru1$G_Q03bn[newPeru1$G_Q03b == "N"] = NA
newPeru1$G_Q03bn[newPeru1$G_Q03b == "1"] = 1
newPeru1$G_Q03bn[newPeru1$G_Q03b == "2"] = 2
newPeru1$G_Q03bn[newPeru1$G_Q03b == "3"] = 3
newPeru1$G_Q03bn[newPeru1$G_Q03b == "4"] = 4
newPeru1$G_Q03bn[newPeru1$G_Q03b == "5"] = 5

# G_Q03c

newPeru1$G_Q03cn[newPeru1$G_Q03c == "N"] = NA
newPeru1$G_Q03cn[newPeru1$G_Q03c == "1"] = 1
newPeru1$G_Q03cn[newPeru1$G_Q03c == "2"] = 2
newPeru1$G_Q03cn[newPeru1$G_Q03c == "3"] = 3
newPeru1$G_Q03cn[newPeru1$G_Q03c == "4"] = 4
newPeru1$G_Q03cn[newPeru1$G_Q03c == "5"] = 5

# G_Q03d

newPeru1$G_Q03dn[newPeru1$G_Q03d == "N"] = NA
newPeru1$G_Q03dn[newPeru1$G_Q03d == "1"] = 1
newPeru1$G_Q03dn[newPeru1$G_Q03d == "2"] = 2
newPeru1$G_Q03dn[newPeru1$G_Q03d == "3"] = 3
newPeru1$G_Q03dn[newPeru1$G_Q03d == "4"] = 4
newPeru1$G_Q03dn[newPeru1$G_Q03d == "5"] = 5

# G_Q03f

newPeru1$G_Q03fn[newPeru1$G_Q03f == "N"] = NA
newPeru1$G_Q03fn[newPeru1$G_Q03f == "1"] = 1
newPeru1$G_Q03fn[newPeru1$G_Q03f == "2"] = 2
newPeru1$G_Q03fn[newPeru1$G_Q03f == "3"] = 3
newPeru1$G_Q03fn[newPeru1$G_Q03f == "4"] = 4
newPeru1$G_Q03fn[newPeru1$G_Q03f == "5"] = 5

# G_Q03g

newPeru1$G_Q03gn[newPeru1$G_Q03g == "N"] = NA
newPeru1$G_Q03gn[newPeru1$G_Q03g == "1"] = 1
newPeru1$G_Q03gn[newPeru1$G_Q03g == "2"] = 2
newPeru1$G_Q03gn[newPeru1$G_Q03g == "3"] = 3
newPeru1$G_Q03gn[newPeru1$G_Q03g == "4"] = 4
newPeru1$G_Q03gn[newPeru1$G_Q03g == "5"] = 5

# G_Q03h

newPeru1$G_Q03hn[newPeru1$G_Q03h == "N"] = NA
newPeru1$G_Q03hn[newPeru1$G_Q03h == "1"] = 1
newPeru1$G_Q03hn[newPeru1$G_Q03h == "2"] = 2
newPeru1$G_Q03hn[newPeru1$G_Q03h == "3"] = 3
newPeru1$G_Q03hn[newPeru1$G_Q03h == "4"] = 4
newPeru1$G_Q03hn[newPeru1$G_Q03h == "5"] = 5

# G_Q04

newPeru1$G_Q04n[newPeru1$G_Q04 == "N"] = NA
newPeru1$G_Q04n[newPeru1$G_Q04 == "1"] = 0
newPeru1$G_Q04n[newPeru1$G_Q04 == "2"] = 1

# G_Q04_T

newPeru1$G_Q04_Tn[newPeru1$G_Q04_T == "N"] = NA
newPeru1$G_Q04_Tn[newPeru1$G_Q04_T == "1"] = 0
newPeru1$G_Q04_Tn[newPeru1$G_Q04_T == "2"] = 1

# G_Q05a

newPeru1$G_Q05an[newPeru1$G_Q05a == "V"] = NA
newPeru1$G_Q05an[newPeru1$G_Q05a == "N"] = NA
newPeru1$G_Q05an[newPeru1$G_Q05a == "1"] = 1
newPeru1$G_Q05an[newPeru1$G_Q05a == "2"] = 2
newPeru1$G_Q05an[newPeru1$G_Q05a == "3"] = 3
newPeru1$G_Q05an[newPeru1$G_Q05a == "4"] = 4
newPeru1$G_Q05an[newPeru1$G_Q05a == "5"] = 5

# G_Q05c

newPeru1$G_Q05cn[newPeru1$G_Q05c == "V"] = NA
newPeru1$G_Q05cn[newPeru1$G_Q05c == "N"] = NA
newPeru1$G_Q05cn[newPeru1$G_Q05c == "1"] = 1
newPeru1$G_Q05cn[newPeru1$G_Q05c == "2"] = 2
newPeru1$G_Q05cn[newPeru1$G_Q05c == "3"] = 3
newPeru1$G_Q05cn[newPeru1$G_Q05c == "4"] = 4
newPeru1$G_Q05cn[newPeru1$G_Q05c == "5"] = 5

#G_Q05d 
newPeru1$G_Q05dn[newPeru1$G_Q05d == "V"] = NA
newPeru1$G_Q05dn[newPeru1$G_Q05d == "N"] = NA
newPeru1$G_Q05dn[newPeru1$G_Q05d == "1"] = 1
newPeru1$G_Q05dn[newPeru1$G_Q05d == "2"] = 2
newPeru1$G_Q05dn[newPeru1$G_Q05d == "3"] = 3
newPeru1$G_Q05dn[newPeru1$G_Q05d == "4"] = 4
newPeru1$G_Q05dn[newPeru1$G_Q05d == "5"] = 5

#G_Q05e

newPeru1$G_Q05en[newPeru1$G_Q05e == "V"] = NA
newPeru1$G_Q05en[newPeru1$G_Q05e == "N"] = NA
newPeru1$G_Q05en[newPeru1$G_Q05e == "1"] = 1
newPeru1$G_Q05en[newPeru1$G_Q05e == "2"] = 2
newPeru1$G_Q05en[newPeru1$G_Q05e == "3"] = 3
newPeru1$G_Q05en[newPeru1$G_Q05e == "4"] = 4
newPeru1$G_Q05en[newPeru1$G_Q05e == "5"] = 5

#G_Q05g 

newPeru1$G_Q05gn[newPeru1$G_Q05g == "V"] = NA
newPeru1$G_Q05gn[newPeru1$G_Q05g == "N"] = NA
newPeru1$G_Q05gn[newPeru1$G_Q05g == "1"] = 1
newPeru1$G_Q05gn[newPeru1$G_Q05g == "2"] = 2
newPeru1$G_Q05gn[newPeru1$G_Q05g == "3"] = 3
newPeru1$G_Q05gn[newPeru1$G_Q05g == "4"] = 4
newPeru1$G_Q05gn[newPeru1$G_Q05g == "5"] = 5

#G_Q05h

newPeru1$G_Q05hn[newPeru1$G_Q05h == "V"] =NA
newPeru1$G_Q05hn[newPeru1$G_Q05h == "N"] =NA
newPeru1$G_Q05hn[newPeru1$G_Q05h == "1"] =1
newPeru1$G_Q05hn[newPeru1$G_Q05h == "2"] =2
newPeru1$G_Q05hn[newPeru1$G_Q05h == "3"] =3
newPeru1$G_Q05hn[newPeru1$G_Q05h == "4"] =4
newPeru1$G_Q05hn[newPeru1$G_Q05h == "5"] =5


#G_Q06

newPeru1$G_Q06n[newPeru1$G_Q06 == "V"] =NA
newPeru1$G_Q06n[newPeru1$G_Q06 == "N"] =NA
newPeru1$G_Q06n[newPeru1$G_Q06 == "R"] =NA
newPeru1$G_Q06n[newPeru1$G_Q06 == "1"] =1
newPeru1$G_Q06n[newPeru1$G_Q06 == "2"] =2
newPeru1$G_Q06n[newPeru1$G_Q06 == "3"] =3
newPeru1$G_Q06n[newPeru1$G_Q06 == "4"] =4
newPeru1$G_Q06n[newPeru1$G_Q06 == "5"] =5

#G_Q07

newPeru1$G_Q07n[newPeru1$G_Q07 == "V"] =NA
newPeru1$G_Q07n[newPeru1$G_Q07 == "N"] =NA
newPeru1$G_Q07n[newPeru1$G_Q07 == "1"] =0
newPeru1$G_Q07n[newPeru1$G_Q07 == "2"] =1

#G_Q08 

newPeru1$G_Q08n[newPeru1$G_Q08 == "V"] =NA
newPeru1$G_Q08n[newPeru1$G_Q08 == "N"] =NA
newPeru1$G_Q08n[newPeru1$G_Q08 == "D"] =NA
newPeru1$G_Q08n[newPeru1$G_Q08 == "R"] =NA
newPeru1$G_Q08n[newPeru1$G_Q08 == "1"] =0
newPeru1$G_Q08n[newPeru1$G_Q08 == "2"] =1

#H_q01a

newPeru1$H_Q01an[newPeru1$H_Q01a == "N"] =NA
newPeru1$H_Q01an[newPeru1$H_Q01a == "1"] =1
newPeru1$H_Q01an[newPeru1$H_Q01a == "2"] =2
newPeru1$H_Q01an[newPeru1$H_Q01a == "3"] =3
newPeru1$H_Q01an[newPeru1$H_Q01a == "4"] =4
newPeru1$H_Q01an[newPeru1$H_Q01a == "5"] =5

#H_q01b

newPeru1$H_Q01bn[newPeru1$H_Q01b == "N"] =NA
newPeru1$H_Q01bn[newPeru1$H_Q01b == "1"] =1
newPeru1$H_Q01bn[newPeru1$H_Q01b == "2"] =2
newPeru1$H_Q01bn[newPeru1$H_Q01b == "3"] =3
newPeru1$H_Q01bn[newPeru1$H_Q01b == "4"] =4
newPeru1$H_Q01bn[newPeru1$H_Q01b == "5"] =5

#H_q01b_T

newPeru1$H_Q01b_Tn[newPeru1$H_Q01b_T == "N"] =NA
newPeru1$H_Q01b_Tn[newPeru1$H_Q01b_T == "1"] =1
newPeru1$H_Q01b_Tn[newPeru1$H_Q01b_T == "2"] =2
newPeru1$H_Q01b_Tn[newPeru1$H_Q01b_T == "3"] =3
newPeru1$H_Q01b_Tn[newPeru1$H_Q01b_T == "4"] =4
newPeru1$H_Q01b_Tn[newPeru1$H_Q01b_T == "5"] =5

#H_q01c

newPeru1$H_Q01cn[newPeru1$H_Q01c == "N"] =NA
newPeru1$H_Q01cn[newPeru1$H_Q01c == "1"] =1
newPeru1$H_Q01cn[newPeru1$H_Q01c == "2"] =2
newPeru1$H_Q01cn[newPeru1$H_Q01c == "3"] =3
newPeru1$H_Q01cn[newPeru1$H_Q01c == "4"] =4
newPeru1$H_Q01cn[newPeru1$H_Q01c == "5"] =5

#H_q01c_T

newPeru1$H_Q01c_Tn[newPeru1$H_Q01c_T == "N"] =NA
newPeru1$H_Q01c_Tn[newPeru1$H_Q01c_T == "1"] =1
newPeru1$H_Q01c_Tn[newPeru1$H_Q01c_T == "2"] =2
newPeru1$H_Q01c_Tn[newPeru1$H_Q01c_T == "3"] =3
newPeru1$H_Q01c_Tn[newPeru1$H_Q01c_T == "4"] =4
newPeru1$H_Q01c_Tn[newPeru1$H_Q01c_T == "5"] =5

#H_q01d

newPeru1$H_Q01dn[newPeru1$H_Q01d == "N"] =NA
newPeru1$H_Q01dn[newPeru1$H_Q01d == "1"] =1
newPeru1$H_Q01dn[newPeru1$H_Q01d == "2"] =2
newPeru1$H_Q01dn[newPeru1$H_Q01d == "3"] =3
newPeru1$H_Q01dn[newPeru1$H_Q01d == "4"] =4
newPeru1$H_Q01dn[newPeru1$H_Q01d == "5"] =5

#H_q01e

newPeru1$H_Q01en[newPeru1$H_Q01e == "N"] =NA
newPeru1$H_Q01en[newPeru1$H_Q01e == "R"] =NA
newPeru1$H_Q01en[newPeru1$H_Q01e == "1"] =1
newPeru1$H_Q01en[newPeru1$H_Q01e == "2"] =2
newPeru1$H_Q01en[newPeru1$H_Q01e == "3"] =3
newPeru1$H_Q01en[newPeru1$H_Q01e == "4"] =4
newPeru1$H_Q01en[newPeru1$H_Q01e == "5"] =5

#H_q01e_T

newPeru1$H_Q01e_Tn[newPeru1$H_Q01e_T == "N"] =NA
newPeru1$H_Q01e_Tn[newPeru1$H_Q01e_T == "R"] =NA
newPeru1$H_Q01e_Tn[newPeru1$H_Q01e_T == "1"] =1
newPeru1$H_Q01e_Tn[newPeru1$H_Q01e_T == "2"] =2
newPeru1$H_Q01e_Tn[newPeru1$H_Q01e_T == "3"] =3
newPeru1$H_Q01e_Tn[newPeru1$H_Q01e_T == "4"] =4
newPeru1$H_Q01e_Tn[newPeru1$H_Q01e_T == "5"] =5

#H_q01f

newPeru1$H_Q01fn[newPeru1$H_Q01f == "N"] =NA
newPeru1$H_Q01fn[newPeru1$H_Q01f == "R"] =NA
newPeru1$H_Q01fn[newPeru1$H_Q01f == "1"] =1
newPeru1$H_Q01fn[newPeru1$H_Q01f == "2"] =2
newPeru1$H_Q01fn[newPeru1$H_Q01f == "3"] =3
newPeru1$H_Q01fn[newPeru1$H_Q01f == "4"] =4
newPeru1$H_Q01fn[newPeru1$H_Q01f == "5"] =5

#H_q01g

newPeru1$H_Q01gn[newPeru1$H_Q01g == "N"] =NA
newPeru1$H_Q01gn[newPeru1$H_Q01g == "1"] =1
newPeru1$H_Q01gn[newPeru1$H_Q01g == "2"] =2
newPeru1$H_Q01gn[newPeru1$H_Q01g == "3"] =3
newPeru1$H_Q01gn[newPeru1$H_Q01g == "4"] =4
newPeru1$H_Q01gn[newPeru1$H_Q01g == "5"] =5

#H_q01h 

newPeru1$H_Q01hn[newPeru1$H_Q01h== "1"] = 1
newPeru1$H_Q01hn[newPeru1$H_Q01h== "2"] = 2
newPeru1$H_Q01hn[newPeru1$H_Q01h== "3"] = 3
newPeru1$H_Q01hn[newPeru1$H_Q01h== "4"] = 4
newPeru1$H_Q01hn[newPeru1$H_Q01h== "5"] = 5
newPeru1$H_Q01hn[newPeru1$H_Q01h== "N"] = NA

#H_q02a

newPeru1$H_Q02an[newPeru1$H_Q02a== "1"] = 1
newPeru1$H_Q02an[newPeru1$H_Q02a== "2"] = 2
newPeru1$H_Q02an[newPeru1$H_Q02a== "3"] = 3
newPeru1$H_Q02an[newPeru1$H_Q02a== "4"] = 4
newPeru1$H_Q02an[newPeru1$H_Q02a== "5"] = 5
newPeru1$H_Q02an[newPeru1$H_Q02a== "N"] = NA

#H_q02b

newPeru1$H_Q02bn[newPeru1$H_Q02b== "1"] = 1
newPeru1$H_Q02bn[newPeru1$H_Q02b== "2"] = 2
newPeru1$H_Q02bn[newPeru1$H_Q02b== "3"] = 3
newPeru1$H_Q02bn[newPeru1$H_Q02b== "4"] = 4
newPeru1$H_Q02bn[newPeru1$H_Q02b== "5"] = 5
newPeru1$H_Q02bn[newPeru1$H_Q02b== "N"] = NA

#H_q02c

newPeru1$H_Q02cn[newPeru1$H_Q02c== "1"] = 1
newPeru1$H_Q02cn[newPeru1$H_Q02c== "2"] = 2
newPeru1$H_Q02cn[newPeru1$H_Q02c== "3"] = 3
newPeru1$H_Q02cn[newPeru1$H_Q02c== "4"] = 4
newPeru1$H_Q02cn[newPeru1$H_Q02c== "5"] = 5
newPeru1$H_Q02cn[newPeru1$H_Q02c== "N"] = NA

#H_q02d

newPeru1$H_Q02dn[newPeru1$H_Q02d== "1"] = 1
newPeru1$H_Q02dn[newPeru1$H_Q02d== "2"] = 2
newPeru1$H_Q02dn[newPeru1$H_Q02d== "3"] = 3
newPeru1$H_Q02dn[newPeru1$H_Q02d== "4"] = 4
newPeru1$H_Q02dn[newPeru1$H_Q02d== "5"] = 5
newPeru1$H_Q02dn[newPeru1$H_Q02d== "N"] = NA

#H_q03b

newPeru1$H_Q03bn[newPeru1$H_Q03b== "1"] = 1
newPeru1$H_Q03bn[newPeru1$H_Q03b== "2"] = 2
newPeru1$H_Q03bn[newPeru1$H_Q03b== "3"] = 3
newPeru1$H_Q03bn[newPeru1$H_Q03b== "4"] = 4
newPeru1$H_Q03bn[newPeru1$H_Q03b== "5"] = 5
newPeru1$H_Q03bn[newPeru1$H_Q03b== "N"] = NA

#H_q03c

newPeru1$H_Q03cn[newPeru1$H_Q03c== "1"] = 1
newPeru1$H_Q03cn[newPeru1$H_Q03c== "2"] = 2
newPeru1$H_Q03cn[newPeru1$H_Q03c== "3"] = 3
newPeru1$H_Q03cn[newPeru1$H_Q03c== "4"] = 4
newPeru1$H_Q03cn[newPeru1$H_Q03c== "5"] = 5
newPeru1$H_Q03cn[newPeru1$H_Q03c== "D"] = NA
newPeru1$H_Q03cn[newPeru1$H_Q03c== "N"] = NA

#H_q03d

newPeru1$H_Q03dn[newPeru1$H_Q03d== "1"] = 1
newPeru1$H_Q03dn[newPeru1$H_Q03d== "2"] = 2
newPeru1$H_Q03dn[newPeru1$H_Q03d== "3"] = 3
newPeru1$H_Q03dn[newPeru1$H_Q03d== "4"] = 4
newPeru1$H_Q03dn[newPeru1$H_Q03d== "5"] = 5
newPeru1$H_Q03dn[newPeru1$H_Q03d== "N"] = NA

#H_q03f

newPeru1$H_Q03fn[newPeru1$H_Q03f== "1"] = 1
newPeru1$H_Q03fn[newPeru1$H_Q03f== "2"] = 2
newPeru1$H_Q03fn[newPeru1$H_Q03f== "3"] = 3
newPeru1$H_Q03fn[newPeru1$H_Q03f== "4"] = 4
newPeru1$H_Q03fn[newPeru1$H_Q03f== "5"] = 5
newPeru1$H_Q03fn[newPeru1$H_Q03f== "N"] = NA

#H_q03g

newPeru1$H_Q03gn[newPeru1$H_Q03g== "1"] = 1
newPeru1$H_Q03gn[newPeru1$H_Q03g== "2"] = 2
newPeru1$H_Q03gn[newPeru1$H_Q03g== "3"] = 3
newPeru1$H_Q03gn[newPeru1$H_Q03g== "4"] = 4
newPeru1$H_Q03gn[newPeru1$H_Q03g== "5"] = 5
newPeru1$H_Q03gn[newPeru1$H_Q03g== "N"] = NA

#H_q03h

newPeru1$H_Q03hn[newPeru1$H_Q03h== "1"] = 1
newPeru1$H_Q03hn[newPeru1$H_Q03h== "2"] = 2
newPeru1$H_Q03hn[newPeru1$H_Q03h== "3"] = 3
newPeru1$H_Q03hn[newPeru1$H_Q03h== "4"] = 4
newPeru1$H_Q03hn[newPeru1$H_Q03h== "5"] = 5
newPeru1$H_Q03hn[newPeru1$H_Q03h== "N"] = NA

#H_Q04a

newPeru1$H_Q04an[newPeru1$H_Q04a == "V"] =NA
newPeru1$H_Q04an[newPeru1$H_Q04a == "N"] =NA
newPeru1$H_Q04an[newPeru1$H_Q04a == "1"] =0
newPeru1$H_Q04an[newPeru1$H_Q04a == "2"] =1

#H_Q04b

newPeru1$H_Q04bn[newPeru1$H_Q04b == "V"] =NA
newPeru1$H_Q04bn[newPeru1$H_Q04b == "N"] =NA
newPeru1$H_Q04bn[newPeru1$H_Q04b == "1"] =0
newPeru1$H_Q04bn[newPeru1$H_Q04b == "2"] =1

#H_Q05a

newPeru1$H_Q05an[newPeru1$H_Q05a == "V"] =NA
newPeru1$H_Q05an[newPeru1$H_Q05a == "N"] =NA
newPeru1$H_Q05an[newPeru1$H_Q05a == "1"] =1
newPeru1$H_Q05an[newPeru1$H_Q05a == "2"] =2
newPeru1$H_Q05an[newPeru1$H_Q05a == "3"] =3
newPeru1$H_Q05an[newPeru1$H_Q05a == "4"] =4
newPeru1$H_Q05an[newPeru1$H_Q05a == "5"] =5

#H_Q05c

newPeru1$H_Q05cn[newPeru1$H_Q05c == "V"] =NA
newPeru1$H_Q05cn[newPeru1$H_Q05c == "N"] =NA
newPeru1$H_Q05cn[newPeru1$H_Q05c == "1"] =1
newPeru1$H_Q05cn[newPeru1$H_Q05c == "2"] =2
newPeru1$H_Q05cn[newPeru1$H_Q05c == "3"] =3
newPeru1$H_Q05cn[newPeru1$H_Q05c == "4"] =4
newPeru1$H_Q05cn[newPeru1$H_Q05c == "5"] =5

#H_Q05d

newPeru1$H_Q05dn[newPeru1$H_Q05d == "V"] =NA
newPeru1$H_Q05dn[newPeru1$H_Q05d == "N"] =NA
newPeru1$H_Q05dn[newPeru1$H_Q05d == "1"] =1
newPeru1$H_Q05dn[newPeru1$H_Q05d == "2"] =2
newPeru1$H_Q05dn[newPeru1$H_Q05d == "3"] =3
newPeru1$H_Q05dn[newPeru1$H_Q05d == "4"] =4
newPeru1$H_Q05dn[newPeru1$H_Q05d == "5"] =5

#H_Q05e

newPeru1$H_Q05en[newPeru1$H_Q05e == "V"] =NA
newPeru1$H_Q05en[newPeru1$H_Q05e == "N"] =NA
newPeru1$H_Q05en[newPeru1$H_Q05e == "1"] =1
newPeru1$H_Q05en[newPeru1$H_Q05e == "2"] =2
newPeru1$H_Q05en[newPeru1$H_Q05e == "3"] =3
newPeru1$H_Q05en[newPeru1$H_Q05e == "4"] =4
newPeru1$H_Q05en[newPeru1$H_Q05e == "5"] =5

#H_Q05f

newPeru1$H_Q05fn[newPeru1$H_Q05f == "V"] =NA
newPeru1$H_Q05fn[newPeru1$H_Q05f == "N"] =NA
newPeru1$H_Q05fn[newPeru1$H_Q05f == "1"] =1
newPeru1$H_Q05fn[newPeru1$H_Q05f == "2"] =2
newPeru1$H_Q05fn[newPeru1$H_Q05f == "3"] =3
newPeru1$H_Q05fn[newPeru1$H_Q05f == "4"] =4
newPeru1$H_Q05fn[newPeru1$H_Q05f == "5"] =5

#H_Q05g

newPeru1$H_Q05gn[newPeru1$H_Q05g == "V"] =NA
newPeru1$H_Q05gn[newPeru1$H_Q05g == "N"] =NA
newPeru1$H_Q05gn[newPeru1$H_Q05g == "1"] =1
newPeru1$H_Q05gn[newPeru1$H_Q05g == "2"] =2
newPeru1$H_Q05gn[newPeru1$H_Q05g == "3"] =3
newPeru1$H_Q05gn[newPeru1$H_Q05g == "4"] =4
newPeru1$H_Q05gn[newPeru1$H_Q05g == "5"] =5

#H_Q05h

newPeru1$H_Q05hn[newPeru1$H_Q05h == "V"] =NA
newPeru1$H_Q05hn[newPeru1$H_Q05h == "N"] =NA
newPeru1$H_Q05hn[newPeru1$H_Q05h == "1"] =1
newPeru1$H_Q05hn[newPeru1$H_Q05h == "2"] =2
newPeru1$H_Q05hn[newPeru1$H_Q05h == "3"] =3
newPeru1$H_Q05hn[newPeru1$H_Q05h == "4"] =4
newPeru1$H_Q05hn[newPeru1$H_Q05h == "5"] =5

#J_Q03a

newPeru1$J_Q03an[newPeru1$J_Q03a == "N"] = NA
newPeru1$J_Q03an[newPeru1$J_Q03a == "1"] = 0
newPeru1$J_Q03an[newPeru1$J_Q03a == "2"] = 1

#J_Q03b

newPeru1$J_Q03bn[newPeru1$J_Q03b == "N"] = NA
newPeru1$J_Q03bn[newPeru1$J_Q03b == "R"] = NA
newPeru1$J_Q03bn[newPeru1$J_Q03b == "V"] = NA
newPeru1$J_Q03bn[newPeru1$J_Q03b == "1"] = 1
newPeru1$J_Q03bn[newPeru1$J_Q03b == "2"] = 2
newPeru1$J_Q03bn[newPeru1$J_Q03b == "3"] = 3
newPeru1$J_Q03bn[newPeru1$J_Q03b == "4"] = 4
newPeru1$J_Q03bn[newPeru1$J_Q03b == "5"] = 5
newPeru1$J_Q03bn[newPeru1$J_Q03b == "6"] = 6
newPeru1$J_Q03bn[newPeru1$J_Q03b == "7"] = 7
newPeru1$J_Q03bn[newPeru1$J_Q03b == "8"] = 8
newPeru1$J_Q03bn[newPeru1$J_Q03b == "9"] = 9
newPeru1$J_Q03bn[newPeru1$J_Q03b == "10"] = 10
newPeru1$J_Q03bn[newPeru1$J_Q03b == "11"] = 11
newPeru1$J_Q03bn[newPeru1$J_Q03b == "12"] = 12
newPeru1$J_Q03bn[newPeru1$J_Q03b == "13"] = 13
newPeru1$J_Q03bn[newPeru1$J_Q03b == "16"] = 16
newPeru1$J_Q03bn[newPeru1$J_Q03b == "19"] = 19

#J_Q06b

newPeru1$J_Q06bn[newPeru1$J_Q06b== "1"] = 1
newPeru1$J_Q06bn[newPeru1$J_Q06b== "2"] = 2
newPeru1$J_Q06bn[newPeru1$J_Q06b== "3"] = 3
newPeru1$J_Q06bn[newPeru1$J_Q06b== "D"] = NA
newPeru1$J_Q06bn[newPeru1$J_Q06b== "N"] = NA
newPeru1$J_Q06bn[newPeru1$J_Q06b== "R"] = NA

#J_Q07b

newPeru1$J_Q07bn[newPeru1$J_Q07b== "1"] = 1
newPeru1$J_Q07bn[newPeru1$J_Q07b== "2"] = 2
newPeru1$J_Q07bn[newPeru1$J_Q07b== "3"] = 3
newPeru1$J_Q07bn[newPeru1$J_Q07b== "D"] = NA
newPeru1$J_Q07bn[newPeru1$J_Q07b== "N"] = NA
newPeru1$J_Q07bn[newPeru1$J_Q07b== "R"] = NA

# Creation of new subset 

subPeru <- newPeru1 %>% 
  select("AGE_R", "GENDER_Rn","B_Q01an", "B_Q01a_Tn", "B_Q02an", "B_Q02cn", "B_Q10cn", "B_Q01bn", "C_Q01an", "C_Q01cn", "C_Q02an", "D_Q03n", "D_Q14n", "D_Q16an", "D_Q18a_T", "F_Q01bn","F_Q02bn","F_Q02cn","F_Q02dn","F_Q02en","F_Q03bn","F_Q04an","F_Q04bn","F_Q05an","F_Q05bn","F_Q07bn","G_Q01an","G_Q02an","G_Q02bn","G_Q02cn","G_Q02dn","G_Q03bn","G_Q03cn","G_Q03dn","G_Q03fn","G_Q03gn","G_Q03hn", "G_Q04n", "G_Q04_Tn", "G_Q05an", "G_Q05cn", "G_Q05dn", "G_Q05en", "G_Q05gn", "G_Q05hn", "G_Q06n", "G_Q07n", "G_Q08n", "H_Q01an", "H_Q01bn", "H_Q01b_Tn", "H_Q01cn", "H_Q01c_Tn", "H_Q01dn", "H_Q01en", "H_Q01e_Tn", "H_Q01fn", "H_Q01gn", "H_Q01hn", "H_Q02an", "H_Q02bn","H_Q02cn", "H_Q02dn", "H_Q03bn", "H_Q03cn", "H_Q03dn", "H_Q03fn", "H_Q03gn", "H_Q03hn","H_Q04an", "H_Q04bn", "H_Q05an", "H_Q05cn", "H_Q05dn", "H_Q05en", "H_Q05fn", "H_Q05gn", "H_Q05hn", "J_Q03an", "J_Q03bn", "J_Q06bn", "J_Q07bn","COMPUTEREXPERIENCE", "MONTHLYINCPR","YEARLYINCPR")

```

<br>

**Dropping NAs**

<br>


```{r}


#Create function to standardize 
standardize= function(x)
{return(x- mean(x, na.rm = TRUE))/ sd(x, na.rm = TRUE)}

#Apply function to the dataset 


std_dataP = as.data.frame(apply(subPeru,2,standardize))

# Creation of the first index of ICT skills for work 

std_dataP$meanict <- (std_dataP$G_Q05an + std_dataP$G_Q05cn + std_dataP$G_Q05dn + std_dataP$G_Q05en + std_dataP$G_Q05gn + std_dataP$G_Q06n + std_dataP$G_Q07n + std_dataP$G_Q08n)/8

# Creation  of a more general index of ICT with only 3  variables 

std_dataP$meanictBasic <- (std_dataP$G_Q04n + std_dataP$G_Q04_Tn + std_dataP$COMPUTEREXPERIENCE)/3

# Index of Education status

std_dataP$meanEducation <- (std_dataP$B_Q01an + std_dataP$B_Q01a_Tn + std_dataP$B_Q02an + std_dataP$B_Q01bn)/4

# Index of Work status

std_dataP$meanWorkS <- (std_dataP$C_Q01an + std_dataP$D_Q03n + std_dataP$D_Q14n + std_dataP$D_Q18a_T)/4

# Index of Work status

std_dataP$meanWorkS <- (std_dataP$C_Q01an + std_dataP$D_Q03n + std_dataP$D_Q14n + std_dataP$D_Q18a_T)/4

# Index of Soft skills 

std_dataP$meanSoftS <- (std_dataP$F_Q01bn + std_dataP$F_Q02bn + std_dataP$F_Q02cn + std_dataP$F_Q02dn + std_dataP$F_Q02en + std_dataP$F_Q03bn + std_dataP$F_Q04an + std_dataP$F_Q05an + std_dataP$F_Q05bn)/9

# Index of Numeracy skills 

std_dataP$meanNumeracyS <- (std_dataP$G_Q03bn + std_dataP$G_Q03cn + std_dataP$G_Q03dn + std_dataP$G_Q03fn + std_dataP$G_Q03gn + std_dataP$G_Q03hn)/6

# Index of Literacy skills 

std_dataP$meanLiteracyS <- (std_dataP$G_Q01an + std_dataP$G_Q02an + std_dataP$G_Q02bn + std_dataP$G_Q02cn + std_dataP$G_Q02dn)/5




#HOLA 

```